---
title: "Jack Mackerel Assessment SCW14"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  word_document:
    reference_docx:  ../../catch/report_template_v1.7.dotx
---

```{r setup, include=FALSE}
assessment_dir <- normalizePath(
  file.path(dirname(knitr::current_input(dir = TRUE)), "..", "..", "assessment"),
  winslash = "/"
)
knitr::opts_knit$set(root.dir = assessment_dir)
# knitr::opts_knit$set(root.dir=file.path(here::here()))
knitr::opts_chunk$set(warning=F, message=F, echo=F, results=F,fig.width=6, fig.height=5)
```

This document was compiled in `RMarkdown`, and shows the incremental results of the Chilean Jack Mackerel (*Trachurus murphyi*) stock assessment benchmark in `r format(Sys.time(), "%Y")`. The files associated with this document can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

Annoted data files can be found in the Excel spreadsheet `newAge.xlsx` on [`jjm/assessment/data`](https://github.com/SPRFMO/jjm/tree/master/assessment/data).

* Compiled the latest `jjm/src/jjms.tpl`
  - This can be done by navigating to the `jjm/src` folder in your Terminal, and using the `make` command
  - You will need to have [ADMB](http://www.admb-project.org/) installed to do this.
  - This does not need to be done if you're only re-compiling the R Markdown document.
* Updated the `jjmR` package
  - This can be done in `R` using the command `remotes::install_github("SPRFMO/jjmR")`


# Model Naming Convention
File naming conventions have been changed to reflect the stock structure hypotheses associated with each run. The `h1` denotes the single-stock hypothesis, while `h2` denotes the two-stock one.

Model      | Description
-----------|--------------
0.00  | Exact 2021 (single stock `h1` and two-stock `h2`) model and data set through 2020 (mod1.0 from SC09)
0.01  | As 0.00 but with the model beginning at age-0.
0.02  | As **0.01** but replacing previous age data with updated data; mean stock weight at age calculated as a mean from SC_Chile 4th quarter, 1995-2020; natural mortality set to 0.25; downweighting DEPM.
0.03  | As **0.00** but replacing previous age data with updated data; mean stock weight at age calculated as a mean from SC_Chile 4th quarter, 1995-2020; natural mortality set to 0.25;  downweighting DEPM.
0.04  | As 0.03 but with L_infinity updated to reflect TL (80.4) instead of FL (74.4); Lo updated to 15.75 to reflect the mean total length of age-1 fish.
------|------
1.00  | As **0.04**.
1.01  | As 1.00 but with changes in selectivity. (JNI)
1.02  | As 1.00 but with age-varying M (Chen and Watanabe method; scaled to 0.28 (average over entire vector)). (NH)
1.03  | As 1.00 but with the new offshore CPUE index that incorporates effort creep. (MP)
1.04  | As 1.00 but with pre-weighted sample sizes for composition data. (IP)
1.05  | As 1.04 but with sample sizes for composition data and CVs of index data based on expert judgement.
1.06    |   As 1.03 but with the Chilean CPUE index that incorporates a 1% effort creep. (NH)
1.07    |   As 1.04 but with the updated CVs on all the indices (Candidate for furture).
1.08    |   As 1.07 but with high weights on composition data (compare francis weights w/ 1.07).
1.09    |   As 1.07 and 1.06 (combination) and updated CVs because the index series had changed
1.10  | As 1.09 with 5x the sample size (ie, 150, 250, 200) for the multinomials (composition data).
j.11  |   As 1.10 but removing recent age compositions from Chile AcousCS.
1.12  | As 1.11 but Francis weights applied only in one iteration.
1.13  | As 1.12 but Francis weights applied second iteration



```{r install_packages, echo=FALSE, cache=FALSE, eval=FALSE}
if(!'devtools' %in% installed.packages()) install.packages('devtools')
devtools::install_github("SPRFMO/jjmR")

if(!'kableExtra' %in% installed.packages()) install.packages('kableExtra')
```

You'll need to be in the `jjm/assessment` directory in order for the code here to run.

```{r pkgs, echo=FALSE}
library(jjmR)
library(tidyverse)
library(kableExtra)

pwd <- getwd()
# if (!grepl(basename(pwd), "assessment", ignore.case = TRUE)) {
#   stop(paste("Set working directory to jjm/assessment"))
# }

geth <- function(mod,h=hyp) paste0(h,"_", mod)

fn.plotind <- function(mods2compare, indname) {
  fn.seldata <- function(x) {
  x$data$Index[,i] %>%
    bind_rows() %>%
    pivot_longer(everything(), names_to="year") %>%
    drop_na() %>%
    mutate(year=as.numeric(year),
            assessment_year=max(year))
  }

  mods <- compareModels(geth(mods2compare, "h2"))
  i <- grep(indname,mods[[1]]$data$Inames)
  dat2use <- list()
  for(m in 1:length(mods)) {
    dat2use[[m]] <- fn.seldata(mods[[m]])
  }

  p <- map_dfr(dat2use, ~as_tibble(.)) %>%
        mutate(assessment_year=as.factor(assessment_year)) %>%
        ggplot(aes(x=year,y=value,colour=assessment_year)) +
        geom_line() +
        theme_minimal() + 
        scale_x_continuous(breaks= scales::pretty_breaks())
  print(p)
}

fixed_bmsy <- function(mod,refpt=5500){
  old_rat <- (mod[[1]]$output[[1]]$msy_mt[,13])
  new_rat <- (mod[[1]]$output[[1]]$msy_mt[,12]/ refpt)
  mod[[1]]$output[[1]]$msy_mt[,13] <- new_rat
  mod[[1]]$output[[1]]$msy_mt[,10] <- refpt
  return(mod)
}

FinModName <- "1.11"

```

```{r eval=FALSE, include=FALSE}

modnm <- "1.12"

tmp1 <- runit(geth(modnm,"h1"),pdf=TRUE,portrait=F,est=TRUE,exec="../src/jjms")

tmp2 <- runit(geth(modnm,"h2"),pdf=TRUE,portrait=F,est=TRUE,exec="../src/jjms")


```


# Updated Age Data

```{r echo=FALSE}
mods2compare <- c("0.00","0.03")
```

## Single-stock hypothesis

```{r, biomass_h1_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h1"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

```{r, recruitment_h1_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

```{r fmort_h1_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

\newpage

## Two-stock hypothesis

```{r, biomass_h2_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1],"h2"), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h2"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

```{r, recruitment_h2_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

```{r fmort_h2_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}

plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

\newpage

# Correcting Growth Parameters

```{r}
mods2compare <- c("0.03","0.04")
```

## Single-stock hypothesis

```{r, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h1"
obj <- compareModels(geth(mods2compare))

plot(obj,combine=T,what="biomass",stack=F,main="Biomass")
```

```{r, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(obj,combine=T,what="recruitment",stack=F,main="Recruitment")
```

```{r fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(obj,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

\newpage

## Two-stock hypothesis

```{r, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1],"h2"), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h2"
obj <- compareModels(geth(mods2compare))

plot(obj,combine=T,what="biomass",stack=F,main="Biomass")
```

```{r, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(obj,combine=T,what="recruitment",stack=F,main="Recruitment")
```

```{r fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}

plot(obj,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


\newpage

# Updated Age Data

```{r}
mods2compare <- c("0.00","1.13")
```

## Single-stock hypothesis

```{r, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h1"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

```{r, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

```{r, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


