# Appendix E. 0.05 Diagnostic Figure Series

This appendix provides the diagnostic figure series for the 0.05 model set. The selection follows the requested annex figure groups and keeps the figures organized by diagnostic purpose.

| Diagnostic group | Annex figures | Appendix content |
|---|---:|---|
| Retrospective patterns | 6-9 | Analytical retrospective diagnostics for spawning biomass and recruitment under the single-stock and two-stock hypotheses. |
| Input weight-at-age sanity check | 12-13 | Fishery and survey input mean weight-at-age series. |
| Composition fits | 14-27 | Fishery age fits, Far North length fits, and survey age fits. |
| Index fits | 28-29 | Single-stock index fits and combined two-stock index fits. |
| Selection patterns | 37-40 | Fishery and survey selectivity patterns under both stock hypotheses. |

```{r}
#| label: setup-appendix-diagnostic-series
#| include: false
suppressPackageStartupMessages(library(jjmR))

knitr::opts_chunk$set(
  fig.width = 11,
  fig.height = 9,
  out.width = "100%"
)

diag_model_id <- "0.05"
diag_h1nm <- geth(diag_model_id, "h1")
diag_h2nm <- geth(diag_model_id, "h2")

diag_config_dir <- file.path("..", "assessment", "config")
diag_input_dir <- file.path("..", "assessment", "input")
diag_output_dir <- file.path("..", "assessment", "results")

diag_required_files <- c(
  file.path(diag_config_dir, paste0(diag_h1nm, ".ctl")),
  file.path(diag_config_dir, paste0(diag_h2nm, ".ctl")),
  file.path(diag_output_dir, paste0(diag_h1nm, ".rep")),
  file.path(diag_output_dir, paste0(diag_h2nm, ".rep")),
  file.path(diag_output_dir, paste0(diag_h1nm, "_retrospective.RData")),
  file.path(diag_output_dir, paste0(diag_h2nm, "_retrospective.RData"))
)
diag_missing <- diag_required_files[!file.exists(diag_required_files)]
if (length(diag_missing)) {
  stop(
    "Missing files required for the 0.05 diagnostic appendix:\n",
    paste(diag_missing, collapse = "\n"),
    call. = FALSE
  )
}

diag_h1_mod <- readJJM(
  diag_h1nm,
  path = diag_config_dir,
  input = diag_input_dir,
  output = diag_output_dir
)
diag_h1_diag <- diagnostics(diag_h1_mod, plot = FALSE)

diag_h2_mod <- readJJM(
  diag_h2nm,
  path = diag_config_dir,
  input = diag_input_dir,
  output = diag_output_dir
)
diag_h2_diag <- diagnostics(diag_h2_mod, plot = FALSE)

diag_retro_env <- new.env(parent = emptyenv())
load(file.path(diag_output_dir, paste0(diag_h1nm, "_retrospective.RData")), envir = diag_retro_env)
diag_h1_retro <- diag_retro_env$output

diag_retro_env <- new.env(parent = emptyenv())
load(file.path(diag_output_dir, paste0(diag_h2nm, "_retrospective.RData")), envir = diag_retro_env)
diag_h2_retro <- diag_retro_env$output
```

## Retrospective Patterns

```{r}
#| label: fig-diag-retro-ssb-h1
#| fig-cap: !expr paste0("Analytical retrospective of spawning biomass from five peel runs based on Model ", diag_h1nm, " under the single-stock hypothesis.")
plot(diag_h1_retro, var = "SSB")
```

```{r}
#| label: fig-diag-retro-r-h1
#| fig-cap: !expr paste0("Analytical retrospective of recruitment from five peel runs based on Model ", diag_h1nm, " under the single-stock hypothesis.")
plot(diag_h1_retro, var = "R")
```

```{r}
#| label: fig-diag-retro-ssb-h2
#| fig-cap: !expr paste0("Analytical retrospective of spawning biomass from five peel runs for the southern stock (top) and Far North stock (bottom), based on Model ", diag_h2nm, " under the two-stock hypothesis.")
#| fig-height: 10
op <- par(no.readonly = TRUE)
on.exit(par(op), add = TRUE)
par(mfrow = c(2, 1), mar = c(3, 4, 2, 1))
plot(diag_h2_retro, var = "SSB")
```

```{r}
#| label: fig-diag-retro-r-h2
#| fig-cap: !expr paste0("Analytical retrospective of recruitment from five peel runs for the southern stock (top) and Far North stock (bottom), based on Model ", diag_h2nm, " under the two-stock hypothesis.")
#| fig-height: 12
op <- par(no.readonly = TRUE)
on.exit(par(op), add = TRUE)
par(mfrow = c(2, 1), mar = c(3, 4, 2, 1))
plot(diag_h2_retro, var = "R")
```

## Input Weight-at-Age Sanity Checks

```{r}
#| label: fig-diag-wtatage-fishery
#| fig-cap: "Mean weights-at-age used for the fisheries in the JJM models. Each line represents an age from 1 to 12."
plot(diag_h1_diag, var = "weightFishery")
```

```{r}
#| label: fig-diag-wtatage-survey
#| fig-cap: "Mean weights-at-age used for the surveys in the JJM models. Each line represents an age from 1 to 12."
plot(diag_h1_diag, var = "weightAge")
```

## Composition Fits

```{r}
#| label: fig-diag-agefits-fsh-h1-n-chile
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to age compositions for the Chilean northern zone fishery under the single-stock hypothesis.")
plot(diag_h1_diag, var = "ageFitsCatch", fleet = "N_Chile")
```

```{r}
#| label: fig-diag-agefits-fsh-h2-n-chile
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to age compositions for the Chilean northern zone fishery under the two-stock hypothesis.")
plot(diag_h2_diag, var = "ageFitsCatch", fleet = "N_Chile")
```

```{r}
#| label: fig-diag-agefits-fsh-h1-sc-chile-ps
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to age compositions for the South-Central Chilean purse-seine fishery under the single-stock hypothesis.")
plot(diag_h1_diag, var = "ageFitsCatch", fleet = "SC_Chile_PS")
```

```{r}
#| label: fig-diag-agefits-fsh-h2-sc-chile-ps
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to age compositions for the South-Central Chilean purse-seine fishery under the two-stock hypothesis.")
plot(diag_h2_diag, var = "ageFitsCatch", fleet = "SC_Chile_PS")
```

```{r}
#| label: fig-diag-agefits-fsh-h1-offshore-trawl
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to age compositions for the offshore trawl fishery under the single-stock hypothesis.")
plot(diag_h1_diag, var = "ageFitsCatch", fleet = "Offshore_Trawl")
```

```{r}
#| label: fig-diag-agefits-fsh-h2-offshore-trawl
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to age compositions for the offshore trawl fishery under the two-stock hypothesis.")
plot(diag_h2_diag, var = "ageFitsCatch", fleet = "Offshore_Trawl")
```

```{r}
#| label: fig-diag-lenfits-fsh-h1-far-north
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to length compositions for the Far North fishery under the single-stock hypothesis.")
plot(diag_h1_diag, var = "lengthFitsCatch")
```

```{r}
#| label: fig-diag-lenfits-fsh-h2-far-north
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to length compositions for the Far North fishery under the two-stock hypothesis.")
plot(diag_h2_diag, var = "lengthFitsCatch")
```

```{r}
#| label: fig-diag-agefits-srv-h1-chile-acouscs
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to age compositions for the South-Central Acoustic survey under the single-stock hypothesis.")
plot(diag_h1_diag, var = "ageFitsSurvey", fleet = "Chile_AcousCS")
```

```{r}
#| label: fig-diag-agefits-srv-h2-chile-acouscs
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to age compositions for the South-Central Acoustic survey under the two-stock hypothesis.")
plot(diag_h2_diag, var = "ageFitsSurvey", fleet = "Chile_AcousCS")
```

```{r}
#| label: fig-diag-agefits-srv-h1-chile-acousn
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to age compositions for the North Chilean Acoustic survey under the single-stock hypothesis.")
plot(diag_h1_diag, var = "ageFitsSurvey", fleet = "Chile_AcousN")
```

```{r}
#| label: fig-diag-agefits-srv-h2-chile-acousn
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to age compositions for the North Chilean Acoustic survey under the two-stock hypothesis.")
plot(diag_h2_diag, var = "ageFitsSurvey", fleet = "Chile_AcousN")
```

```{r}
#| label: fig-diag-agefits-srv-h1-depm
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to age compositions for the Daily Egg Production Method survey under the single-stock hypothesis.")
plot(diag_h1_diag, var = "ageFitsSurvey", fleet = "DEPM")
```

```{r}
#| label: fig-diag-agefits-srv-h2-depm
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to age compositions for the Daily Egg Production Method survey under the two-stock hypothesis.")
plot(diag_h2_diag, var = "ageFitsSurvey", fleet = "DEPM")
```

## Index Fits

```{r}
#| label: fig-diag-indfits-h1
#| fig-cap: !expr paste0("Model ", diag_h1nm, " fit to abundance indices under the single-stock hypothesis. Vertical bars represent two standard deviations around the observations.")
plot(diag_h1_diag, var = "predictedObservedIndices")
```

```{r}
#| label: fig-diag-indfits-h2
#| fig-cap: !expr paste0("Model ", diag_h2nm, " fit to abundance indices under the two-stock hypothesis for the south stock (top) and Far North stock (bottom). Vertical bars represent two standard deviations around the observations.")
#| fig-width: 11
#| fig-height: 11
op <- par(no.readonly = TRUE)
diag_h2_index_file <- file.path(
  knitr::opts_current$get("fig.path"),
  "fig-diag-indfits-h2-combined.png"
)
dir.create(dirname(diag_h2_index_file), recursive = TRUE, showWarnings = FALSE)
png(diag_h2_index_file, width = 11, height = 11, units = "in", res = 144)
par(mfrow = c(2, 1), mar = c(3.4, 4, 2.1, 1))
plot(diag_h2_diag, var = "predictedObservedIndices", stock = 1)
plot(diag_h2_diag, var = "predictedObservedIndices", stock = 2)
par(op)
dev.off()
knitr::include_graphics(diag_h2_index_file)
```

## Selection Patterns

```{r}
#| label: fig-diag-selfsh-h1
#| fig-cap: !expr paste0("Estimated fishery selectivity over time for Model ", diag_h1nm, " under the single-stock hypothesis.")
print(plot_selectivities(get_selectivities(diag_h1_mod)))
```

```{r}
#| label: fig-diag-selfsh-h2
#| fig-cap: !expr paste0("Estimated fishery selectivity over time for Model ", diag_h2nm, " under the two-stock hypothesis.")
print(plot_selectivities(get_selectivities(diag_h2_mod)))
```

```{r}
#| label: fig-diag-selsrv-h1
#| fig-cap: !expr paste0("Estimated survey selectivity over time for Model ", diag_h1nm, " under the single-stock hypothesis.")
plot(diag_h1_mod, what = "selectivity", fleet = "ind", alpha = 0.2, scale = 10)
```

```{r}
#| label: fig-diag-selsrv-h2
#| fig-cap: !expr paste0("Estimated survey selectivity over time for Model ", diag_h2nm, " under the two-stock hypothesis.")
plot(diag_h2_mod, what = "selectivity", fleet = "ind", alpha = 0.2, scale = 10)
```
