---
title: "Task Group (TG) — 2026 Meeting Schedule & Agendas"
format:
  html:
    toc: false
    number-sections: false
---

{{< include _includes/sprfmo-banner.html >}}

**Task Group (TG) — 2026 Meeting Schedule & Agendas**

*Chair: J. Ianelli \| All meetings: Online (Zoom/Teams) \| 14:00–15:30 CET*

*08:00–9:30 Lima (PET) 09:00-10:30 Santiago (CLT)*

------------------------------------------------------------------------

**AT-A-GLANCE SCHEDULE**

```{r}
#| label: tbl-at-a-glance
#| echo: false
#| warning: false
#| message: false

library(gt)

at_a_glance <- data.frame(
  meeting = c("TG-01", "TG-02", "TG-03", "TG-04", "TG-05", "TG-06", "TG-07", "TG-08", "TG-09", "TG-10"),
  date = c(
    "Thu 26 March 2026",
    "Thu 9 April 2026",
    "Thu 30 April 2026",
    "Thu 28 May 2026",
    "Thu 11 June 2026",
    "Thu 9 July 2026",
    "Thu 13 August 2026",
    "Fri 28 August 2026",
    "Thu 8 October 2026",
    "Thu 12 November 2026"
  ),
  topic = c(
    "Post-Commission Kickoff",
    "WP1 Launch & Benchmark Preparation",
    "Final Pre-Benchmark Preparation",
    "Post-Lima / Pre-Intersessional Debrief",
    "Pre-Wageningen Final Preparation",
    "Post-Wageningen: CMP Shortlist Review",
    "Pre-SC14 Draft Review",
    "Final SC14 Paper Sign-off",
    "Post-SC14 Debrief & Commission Prep",
    "WP4 Report Review & Year-End Close"
  ),
  milestone = c(
    "—",
    "→ Leads to: Benchmark Workshop, Lima (May)",
    "→ Leads to: Benchmark Workshop, Lima (~12–16 May)",
    "→ Leads to: MSE-02 draft performance metrics",
    "→ Leads to: MSE Workshop, Wageningen, 15–19 June 2026",
    "→ SC14 paper drafting begins",
    "→ Leads to: SC14 (September 2026)",
    "→ SC14 submission deadline",
    "→ Leads to: Commission decision (Nov/Dec 2026)",
    "→ SC15 / archive"
  ),
  stringsAsFactors = FALSE
)

at_a_glance |>
  gt() |>
  cols_label(
    meeting = "Meeting",
    date = "Date",
    topic = "Topic",
    milestone = "Key Milestone"
  ) |>
  cols_align(align = "left", columns = everything()) |>
  cols_width(
    meeting ~ px(100),
    date ~ px(230),
    topic ~ px(390),
    milestone ~ px(540)
  ) |>
  tab_style(
    style = list(
      cell_fill(color = "#203b6d"),
      cell_text(color = "white", weight = "bold")
    ),
    locations = cells_column_labels(everything())
  ) |>
  tab_style(
    style = list(
      cell_fill(color = "#c9d6e8"),
      cell_text(color = "#203b6d", weight = "bold")
    ),
    locations = cells_body(columns = meeting)
  ) |>
  tab_style(
    style = cell_text(color = "#1a7c73"),
    locations = cells_body(columns = milestone)
  ) |>
  tab_style(
    style = list(cell_borders(sides = "all", color = "#a7c2df", weight = px(1))),
    locations = cells_body(columns = everything())
  ) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(13),
    data_row.padding = px(6),
    column_labels.padding = px(6),
    table.border.top.color = "#a7c2df",
    table.border.bottom.color = "#a7c2df"
  )
```

*Regular = 2nd Thursday of month. Extra = milestone-driven additional call.*

**2026 PROGRAMME MILESTONES (FOR REFERENCE)**

```{r}
#| label: tbl-programme-milestones
#| echo: false
#| warning: false
#| message: false

library(gt)

milestones <- data.frame(
  month = c("May 2026", "Late May 2026", "Jun 15–19", "Sep 2026", "Nov 2026"),
  event = c(
    "Benchmark Workshop — Lima (Peru)",
    "SC Intersessional meeting",
    "MSE Workshop — Wageningen (WMR/NL)",
    "SC14 — Scientific Committee",
    "WP4 final deliverable"
  ),
  deliverable = c(
    "Candidate assessment models",
    "Approved OM for MSE",
    "CMP shortlist",
    "CMP recommendation",
    "Technical report + source code"
  ),
  output_for = c(
    "SC Intersessional",
    "Wageningen workshop",
    "SC14 document",
    "Commission decision",
    "SC15 / archive"
  ),
  stringsAsFactors = FALSE
)

milestones |>
  gt() |>
  cols_label(
    month = "Month",
    event = "Event",
    deliverable = "Deliverable",
    output_for = "Output for"
  ) |>
  cols_align(align = "left", columns = everything()) |>
  cols_width(
    month ~ px(180),
    event ~ px(390),
    deliverable ~ px(380),
    output_for ~ px(270)
  ) |>
  tab_style(
    style = list(
      cell_fill(color = "#203b6d"),
      cell_text(color = "white", weight = "bold")
    ),
    locations = cells_column_labels(everything())
  ) |>
  tab_style(
    style = list(
      cell_fill(color = "#f0e9d6"),
      cell_text(color = "#d48a07", weight = "bold")
    ),
    locations = cells_body(columns = month)
  ) |>
  tab_style(
    style = cell_text(color = "#1a7c73"),
    locations = cells_body(columns = output_for)
  ) |>
  tab_style(
    style = list(cell_borders(sides = "all", color = "#a7c2df", weight = px(1))),
    locations = cells_body(columns = everything())
  ) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(13),
    data_row.padding = px(6),
    column_labels.padding = px(6),
    table.border.top.color = "#a7c2df",
    table.border.bottom.color = "#a7c2df"
  )
```

**  **

**SPRFMO Jack Mackerel MSE — Technical Group (TG) Session Agenda Plan 2026**

Five 2-hour TG sessions (March–June 2026) leading to the Lima Benchmark (early May) and the Wageningen MSE Workshop (16 June). Each session covers topics for discussion and decisions; where consensus cannot be reached, the decision is deferred one session. Based on Carruthers et al. (2024) MSE roadmap phases.

**Colour legend:** White = discussion topics <span style="color:#9a7b00;">Yellow = items requiring decision</span> <span style="color:#666666;">Grey = pre-meeting preparation</span> <span style="color:#1f5fae;">Blue = linked working papers</span>

```{r}
#| label: tbl-tg-session-plan
#| echo: false
#| warning: false
#| message: false

library(gt)

bullet_list <- function(items, strong = FALSE) {
  prefix <- if (strong) "<li style='margin:0 0 0.2em 0;'><strong>" else "<li style='margin:0 0 0.2em 0;'>"
  suffix <- if (strong) "</strong></li>" else "</li>"
  paste0(
    "<ul style='margin:0; padding-left:1.1em;'>",
    paste0(prefix, items, suffix, collapse = ""),
    "</ul>"
  )
}

agenda <- data.frame(
  session = c(
    "TG-01  \u2014  26 Mar 2026 15:00 CET",
    "TG-02  \u2014  9 Apr 2026 15:00 CEST",
    "TG-03  \u2014  30 Apr 2026 15:00 CEST",
    "TG-04  \u2014  28 May 2026 15:00 CEST",
    "TG-05  \u2014  11 Jun 2026 15:00 CEST"
  ),
  tc = c("1", "2", "3", "4", "5"),
  date = c(
    "26 Mar<br>2026<br>15:00<br>CET",
    "9 Apr<br>2026<br>15:00<br>CEST",
    "30 Apr<br>2026<br>15:00<br>CEST",
    "28 May<br>2026<br>15:00<br>CEST",
    "11 Jun<br>2026<br>15:00<br>CEST"
  ),
  main = c(
    bullet_list(c(
      "Review & endorse working paper plan (10 WPs: Benchmark, Wageningen, SC14)",
      "Sequence and allocation of technical topics across TG-02 to TG-05",
      "Identify which decisions need two sessions (prepare \u2192 conclude)"
    )),
    bullet_list(c(
      "Selectivity: block-based alternatives (SCW16-01 \u00a76.1) vs time-varying; fleet implications",
      "Reference points: fixed RPs vs dynamic BMSY/FMSY \u2014 pros, cons, RFMO precedent",
      "S-R alternatives: simplified options (single BH, regime variants) from SCW16-01 \u00a76.2 \u2014 initial reaction",
      "Indices (SCW16-03): inventory of all 7, CPUE standardisation, index\u2013biomass proportionality",
      "Uncertainty dimensions most consequential for long-term projections"
    )),
    bullet_list(c(
      "CONCLUDE selectivity: agree block structure(s) for OM conditioning",
      "CONCLUDE reference points: agree fixed benchmark RPs; document rationale",
      "Far North treatment (SCW16-01 \u00a76.4): options for h1/h2 consistency",
      "OM grid design (SCW16-04): reference set vs robustness set; which uncertainty axes in each tier",
      "Benchmark handoff: define minimum outputs needed for TG-04 to proceed"
    )),
    bullet_list(c(
      "Lima Benchmark debrief: model simplification, indices, OM design \u2014 what was agreed and what remains open",
      "CRITICAL FORK: Recondition on Benchmark OM outputs OR proceed with SC13-based OM",
      "Stock-hypothesis: using base case + robustness tests to derive advice; attempt consensus",
      "Performance metrics (MSE-02): conservation (P(B<BLIM), P(B<BMSY)), yield (avg catch, AAV), stability metrics",
      "MP families: candidate model-free (DLMtool) and model-based (multi-index, surplus production)"
    )),
    bullet_list(c(
      "CONCLUDE stock-hypothesis: close from TG-04 (or confirm fallback)",
      "CONCLUDE performance metrics: finalise metric list, time horizons, risk tolerance for Wageningen",
      "MP specifications (MSE-01): technical freeze \u2014 data streams, tuning targets, HCR, Buffer/K60",
      "Robustness scenario matrix: finalise all scenarios entering Wageningen (MSE-03)",
      "Cross-platform validation: FLR vs RTMB/OpenMSE \u2014 metrics, responsibilities (WMR/CHL/PER), timeline",
      "Wageningen logistics: trade-off format (Slick, worm plots, Kobe-style); decision-making protocol"
    ))
  ),
  decision = c(
    bullet_list(c(
      "Endorse WP plan; confirm all lead authors (SCW16-03 needs volunteer)",
      "Agree topic schedule TG-02 through TG-05 \u2014 frames all subsequent work"
    ), strong = TRUE),
    bullet_list(c(
      "Discuss selectivity block options \u2014 narrow to \u22642 candidates (conclude TG-03)",
      "Discuss reference point approach \u2014 identify preferred direction (conclude TG-03)",
      "Confirm SCW16-03 lead and scope; agree index standardisation methodology"
    ), strong = TRUE),
    bullet_list(c(
      "Agree selectivity block structure for OM (carried from TG-02)",
      "Agree fixed reference point approach (carried from TG-02)",
      "Agree harmonised Far North treatment for both stock hypotheses",
      "Agree OM grid structure: axes, tiers (reference set vs robustness set)",
      "Agree criteria for OM reconditioning decision at TG-04"
    ), strong = TRUE),
    bullet_list(c(
      "CRITICAL: Recondition OM on Benchmark outputs OR proceed with SC13-based OM \u2014 gates Wageningen scope",
      "Agree S-R priors (steepness, \u03c3R) and recruitment regime treatment across all OMs",
      "Discuss stock-hypothesis treatment for advice \u2014 to conclude at TG-05",
      "Endorse draft performance metrics and time horizons (5/10/20+ yr) \u2014 to finalise at TG-05"
    ), strong = TRUE),
    bullet_list(c(
      "Conclude stock-hypothesis (from TG-04)",
      "Finalise performance metrics list, time horizons and risk tolerance",
      "Freeze MP specifications: no new MPs added after this TG",
      "Agree complete robustness scenario matrix (reference set + robustness set)",
      "Agree cross-platform validation protocol and assign responsibilities",
      "Agree Wageningen communication and decision-making format"
    ), strong = TRUE)
  ),
  prep = c(
    "<em>Chair circulates: SCW16-01 draft, SCW16-02 draft, WP plan, Carruthers roadmap summary, proposed topic allocation. All \u22655 working days before.</em>",
    "<em>SCW16-01 \u00a76.1\u20136.3 fitted diagnostics; SCW16-03 outline; updated topic schedule from TG-01</em>",
    "<em>SCW16-01 \u00a76.4 draft; SCW16-03 first full draft; SCW16-04 outline with OM grid sketch; Chair circulates 'Benchmark handoff checklist'</em>",
    "<em>Lima Benchmark summary circulated after meeting; BM MSE-02 draft performance metrics</em>",
    "<em>Full drafts MSE-01 and MSE-03; Slick/trade-off prototype if available; updated OM status note from WMR</em>"
  ),
  wps = c(
    "SCW16-01<br>SCW16-02<br>Plan doc",
    "SCW16-01<br>SCW16-03",
    "SCW16-01<br>SCW16-03<br>SCW16-04",
    "SCW16-04<br>MSE-02<br>SCW16-01 outcomes",
    "MSE-01<br>MSE-02<br>MSE-03"
  ),
  stringsAsFactors = FALSE
)

agenda |>
  gt(groupname_col = "session") |>
  cols_label(
    tc = "TC",
    date = "Date",
    main = "Main Topics for Discussion",
    decision = "Topics Requiring Decision",
    prep = "Pre-meeting Prep",
    wps = "WPs"
  ) |>
  fmt(
    columns = c(date, main, decision, prep, wps),
    fns = function(x) lapply(x, html)
  ) |>
  cols_align(align = "center", columns = c(tc, date, wps)) |>
  cols_align(align = "left", columns = c(main, decision, prep)) |>
  cols_width(
    tc ~ px(42),
    date ~ px(95),
    main ~ px(380),
    decision ~ px(320),
    prep ~ px(290),
    wps ~ px(90)
  ) |>
  tab_style(
    style = list(
      cell_fill(color = "#203b6d"),
      cell_text(color = "white", weight = "bold")
    ),
    locations = cells_column_labels(everything())
  ) |>
  tab_style(
    style = list(
      cell_fill(color = "#203b6d"),
      cell_text(color = "white", weight = "bold", align = "center")
    ),
    locations = cells_row_groups()
  ) |>
  tab_style(
    style = cell_fill(color = "#fff4bf"),
    locations = cells_body(columns = decision)
  ) |>
  tab_style(
    style = cell_fill(color = "#efefef"),
    locations = cells_body(columns = prep)
  ) |>
  tab_style(
    style = cell_text(color = "#1f5fae", weight = "bold"),
    locations = cells_body(columns = wps)
  ) |>
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = c(main, decision, prep))
  ) |>
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = c(tc, date, wps))
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(columns = tc)
  ) |>
  tab_style(
    style = list(cell_borders(sides = "all", color = "#bfbfbf", weight = px(1))),
    locations = cells_body(columns = everything())
  ) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(12),
    data_row.padding = px(3),
    row_group.padding = px(2),
    column_labels.padding = px(4),
    table.border.top.color = "#bfbfbf",
    table.border.bottom.color = "#bfbfbf"
  )
```

**Notes:** *(1) If Lima Benchmark endorses reconditioning the OM, TG-04 agenda must adjust to incorporate benchmark outcomes before Wageningen. (2) The stock-hypothesis weighting decision (TG-04) is a potential sticking point — plan extra time or a dedicated sub-group call if no consensus at TG-03. (3) All working paper drafts should be circulated at least 5 working days before each TG.*
