---
title: "Jack Mackerel Assessment SCW16"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    code-fold: true
    code-summary: "Show code"
    fig-cap-location: bottom
    number-sections: true
    theme: readable
    toc: true
    toc-depth: 3
    toc-location: right
    lightbox: true
---

{{< include _includes/sprfmo-banner.html >}}

```{=html}
<div class="paper-title">Jack Mackerel Assessment SCW16</div>
```

```{r setup, include=FALSE}
assessment_dir <- normalizePath(
  file.path(dirname(knitr::current_input(dir = TRUE)), "..", "assessment"),
  winslash = "/"
)
knitr::opts_knit$set(root.dir = assessment_dir)
knitr::opts_chunk$set(warning=F, message=F, echo=F, results=F,fig.width=6, fig.height=5)
```

This document was originally compiled in `RMarkdown` then converted into Quarto (a different flavor of markdown). It now tracks the SCW16 benchmark model sequence for Chilean jack mackerel (*Trachurus murphyi*), beginning with the documented `1.14` model series and moving to the candidate `2.00` benchmark pair. The files associated with this document can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

The code to create the input files for this assessment and to run these models can be found in [`jjm/assessment/R/SC13_Bridging.R`](https://github.com/SPRFMO/jjm/tree/master/assessment/R/SC13_Bridging.R). Should you choose to run the models, please ensure that you have:

* Compiled the latest `jjm/src/jjms.tpl`
  - This can be done by navigating to the `jjm/src` folder in your Terminal, and using the `make` command
  - You will need to have [ADMB](http://www.admb-project.org/) installed to do this.
  - This does not need to be done if you're only re-compiling the R Markdown document.
* Updated the `jjmR` package
  - This can be done in `R` using the command `remotes::install_github("SPRFMO/jjmR")`

```{r install_packages, eval=F, cache=F, echo=T}
if(!'devtools' %in% installed.packages()) install.packages('devtools')
devtools::install_github("SPRFMO/jjmR")

if(!'kableExtra' %in% installed.packages()) install.packages('kableExtra')
```

```{r pkgs, echo=T}
library(jjmR)
library(tidyverse)
library(patchwork)
has_kableExtra <- requireNamespace("kableExtra", quietly = TRUE)
theme_set(theme_jjm(base_size = 15))

pwd <- getwd()

fn_seldata <- function(x, i) {
  x$data$Index[,i] %>%
    bind_rows() %>%
    pivot_longer(everything(), names_to = "year") %>%
    drop_na() %>%
    mutate(
      year = as.numeric(year),
      assessment_year = ifelse(
        i==7,
        max(year)+1,
        max(year)
      )
    )
} 

fn_plotind <- function(mods2compare, indname) {
  mods <- compareModels(geth(mods2compare, "h1"))
  i <- grep(indname,mods[[1]]$data$Inames)
  dat2use <- list()
  for(m in 1:length(mods)) {
    dat2use[[m]] <- fn_seldata(mods[[m]],i)
  }

  p <- map_dfr(dat2use, ~as_tibble(.)) %>%
    mutate(assessment_year=as.factor(assessment_year)) %>%
    ggplot() +
      geom_line(aes(x=year,y=value,colour=assessment_year)) +
      scale_x_continuous(breaks= scales::pretty_breaks())
  print(p)
}

model_file_status <- function(model_name) {
  tibble(
    model = model_name,
    control_file = file.exists(file.path("config", paste0(model_name, ".ctl"))),
    data_file = file.exists(file.path("input", paste0(str_remove(model_name, "^h[12]_"), ".dat"))),
    report_file = file.exists(file.path("results", paste0(model_name, ".rep"))),
    yield_file = file.exists(file.path("results", paste0(model_name, ".yld")))
  )
}

style_status_table <- function(x) {
  tab <- knitr::kable(x)
  if (has_kableExtra) {
    tab <- tab %>%
      kableExtra::kable_styling() %>%
      kableExtra::row_spec(0, bold = TRUE, background = "#05427b", color = "white")
  }
  tab
}

reference_model <- "1.14"
candidate_model <- "2.00"
candidate_pair <- paste0(c("h1_", "h2_"), candidate_model)
candidate_pair_available <- all(model_file_status(candidate_pair)$report_file)
finmodname <- if (candidate_pair_available) candidate_model else reference_model

yr_prev <- as.numeric(format(Sys.time(), "%Y"))-1
yr_curr <- as.numeric(format(Sys.time(), "%Y"))

```


# Model Naming Convention
File naming conventions have been changed to reflect the stock structure hypotheses associated with each run. The `h1` denotes the single-stock hypothesis, while `h2` denotes the two-stock one.

For SCW16, the benchmark work is being reorganized around two paired model
series:

* `h1_1.14` and `h2_1.14` are the documented reference models from the SC13
  update sequence. They provide the immediate baseline for biological inputs,
  index treatment, selectivity changes, and FarNorth weight-at-age corrections.
* `h1_0.00` and `h2_0.00` relabel the `1.14` reference pair as the SCW16
  data-update baseline. The `0.00.dat` file is the `1.14.dat` base data file,
  so the `h1_1.14` and `h2_1.14` outputs remain the reference output pair for
  the first comparisons until the relabeled `0.00` controls are explicitly
  rerun.
* `h1_0.01` and `h2_0.01` replace the South-Central Chile fishery CPUE
  (`Chile_CPUE`) with the 1998-2025 standardized series using weighted CVs.
* `h1_0.02` and `h2_0.02` replace the FarNorth-associated CPUE
  (`Peru_CPUE`) with the 2015-2025 series after the Chile CPUE replacement.
* `h1_0.03` and `h2_0.03` replace the FarNorth fishery length-composition
  data with the 1972-2025 series after the FarNorth-associated CPUE
  replacement.
* `h1_0.04` and `h2_0.04` remove the Peru acoustic index from the
  `0.03` data set while retaining the new 2015-2025 FarNorth-associated
  CPUE series as `Peru_CPUE`.
* `h1_0.05` and `h2_0.05` add the split Peru acoustic seasonal survey
  indices as `Peru_Acoust_S1` and `Peru_Acoust_S2`, with length-composition
  data and independent survey selectivity blocks for each new index.
* `h1_2.00` and `h2_2.00` define the active SCW16 benchmark candidate pair.
  This active report keeps those candidate files visible while the incremental
  `0.xx` data-replacement sequence is developed.

```{r scw16_model_series_status, results = "asis"}
scw16_model_series <- tibble(
  model = c("h1_1.14", "h2_1.14", "h1_2.00", "h2_2.00"),
  hypothesis = c("Single-stock", "Two-stock", "Single-stock", "Two-stock"),
  series = c("Reference", "Reference", "SCW16 candidate", "SCW16 candidate"),
  role = c(
    "Reference single-stock model from the 1.14 sequence",
    "Reference two-stock model from the 1.14 sequence",
    "Candidate single-stock benchmark baseline",
    "Candidate two-stock benchmark baseline"
  )
)

scw16_model_series_status <- map_dfr(scw16_model_series$model, model_file_status)

scw16_model_series <- scw16_model_series %>%
  left_join(scw16_model_series_status, by = "model") %>%
  mutate(
    status = case_when(
      control_file & data_file & report_file ~ "available",
      control_file & data_file ~ "configured; results pending",
      data_file ~ "data available; control/results pending",
      TRUE ~ "pending"
    )
  )

scw16_model_series %>%
  select(model, hypothesis, series, role, control_file, data_file, report_file, status) %>%
  style_status_table()
```

```{r scw16_data_replacement_runs, results = "asis"}
scw16_data_runs <- tibble(
  step = c("0.00", "0.01", "0.02", "0.03", "0.04", "0.05"),
  update = c(
    "Relabeled 1.14 reference data and controls as the SCW16 data-update baseline",
    "Replaced South-Central Chile CPUE (`Chile_CPUE`) with the 1998-2025 standardized series; observation errors are mean CPUE times the weighted CV",
    "Replaced the FarNorth-associated CPUE (`Peru_CPUE`) with the 2015-2025 series and supplied standard errors",
    "Replaced the FarNorth fishery length-composition data with the 1972-2025 series using 10-49 cm bins and a 50 cm plus group",
    "Removed the Peru acoustic index from the `0.03` data set",
    "Added split Peru acoustic seasonal survey indices `Peru_Acoust_S1` and `Peru_Acoust_S2` with independent survey selectivities and length-composition data"
  ),
  source = c(
    "input/1.14.dat",
    "data/chile_cpue_2025.tsv",
    "data/farnorth_cpue_2025.tsv",
    "data/farnorth_length_composition_long.tsv; data/farnorth_sample_sizes_scaled_for_mod0.4.csv",
    "input/0.04.dat",
    "R/make_0_05_from_0_04.R; input/0.05.dat"
  ),
  h1_model = paste0("h1_", step),
  h2_model = paste0("h2_", step),
  note = c(
    "0.00 controls/data are available; reference outputs shown from h*_1.14",
    "Fit outputs available",
    "Fit outputs available",
    "Fit outputs available",
    "Fit outputs available",
    "Fit outputs available; h1 nll 4487.731, h2 nll 4392.909"
  )
)

scw16_data_run_status <- scw16_data_runs %>%
  mutate(
    h1_report_file = map_lgl(h1_model, ~model_file_status(.x)$report_file),
    h2_report_file = map_lgl(h2_model, ~model_file_status(.x)$report_file),
    status = case_when(
      step == "0.00" ~ "configured; reference outputs from 1.14",
      h1_report_file & h2_report_file ~ "fit outputs available",
      TRUE ~ "configured; results pending"
    )
  )

scw16_data_run_status %>%
  select(step, update, source, h1_model, h2_model, h1_report_file, h2_report_file, status, note) %>%
  style_status_table()
```



The full historical SC13 bridging table and incremental update sections are omitted from this working SCW16 version so that the report starts with the current paired reference models while tracking the active SCW16 data-replacement and candidate benchmark sequences.

You will need to be in the `jjm/assessment` directory in order for the code here to run.

# SCW16 Data Replacement Sequence

The fitted data-replacement steps are compared against the `1.14`
reference outputs. The relabeled `0.00` files are the SCW16 data-update baseline
inputs, but the figures below use the existing `h1_1.14` and `h2_1.14` outputs
as the reference until the `0.00` controls are explicitly rerun.

```{r mods_compare_scw16_cpue}
data_update_mods <- c(reference_model, "0.01", "0.02", "0.03", "0.04", "0.05")
data_update_h1_cap <- "from the h1_1.14 reference model through the h1_0.05 data-replacement run."
data_update_h2_cap <- "from the h2_1.14 reference model through the h2_0.05 data-replacement run."
```

## Single-stock data-replacement sequence

::: {.panel-tabset}
### Biomass
```{r scw16_cpue_h1_biomass, fig.cap=paste0("Plot comparing biomass estimates ", data_update_h1_cap)}
h1_data_update_ready <- all(model_file_status(geth(data_update_mods, "h1"))$report_file)
if (h1_data_update_ready) {
  hyp <- "h1"
  data_update_h1 <- compareModels(geth(data_update_mods, "h1"))
  plot(data_update_h1, combine = TRUE, what = "biomass", stack = FALSE, main = "Biomass")
} else {
  message("Single-stock data-replacement comparison pending: one or more h1 data-update results are not available.")
}
```

### Recruitment
```{r scw16_cpue_h1_recruitment, fig.cap=paste0("Plot comparing recruitment estimates ", data_update_h1_cap)}
if (h1_data_update_ready) {
  plot(data_update_h1, combine = TRUE, what = "recruitment", stack = FALSE, main = "Recruitment")
}
```

### Fishing Mortality
```{r scw16_cpue_h1_fmort, fig.cap=paste0("Plot comparing fishing mortality estimates ", data_update_h1_cap)}
if (h1_data_update_ready) {
  plot(data_update_h1, combine = TRUE, what = "ftot", stack = FALSE, main = "Total Fishing Mortality")
}
```
:::

## Two-stock data-replacement sequence

::: {.panel-tabset}
### Biomass
```{r scw16_cpue_h2_biomass, fig.cap=paste0("Plot comparing biomass estimates ", data_update_h2_cap)}
h2_data_update_ready <- all(model_file_status(geth(data_update_mods, "h2"))$report_file)
if (h2_data_update_ready) {
  hyp <- "h2"
  data_update_h2 <- compareModels(geth(data_update_mods, "h2"))
  plot(data_update_h2, combine = TRUE, what = "biomass", stack = FALSE, main = "Biomass")
} else {
  message("Two-stock data-replacement comparison pending: one or more h2 data-update results are not available.")
}
```

### Recruitment
```{r scw16_cpue_h2_recruitment, fig.cap=paste0("Plot comparing recruitment estimates ", data_update_h2_cap)}
if (h2_data_update_ready) {
  plot(data_update_h2, combine = TRUE, what = "recruitment", stack = FALSE, main = "Recruitment")
}
```

### Fishing Mortality
```{r scw16_cpue_h2_fmort, fig.cap=paste0("Plot comparing fishing mortality estimates ", data_update_h2_cap)}
if (h2_data_update_ready) {
  plot(data_update_h2, combine = TRUE, what = "ftot", stack = FALSE, main = "Total Fishing Mortality")
}
```
:::

# Reference and Candidate Model Comparison

The initial SCW16 benchmark comparison is from the `1.14` reference pair to the
`2.00` candidate pair. This section is intended to become the main bridge
between the documented SC13 update sequence and the benchmark model sequence. The report lists the paired two-stock candidate even when `h2_2.00.ctl` and its output are still pending.

```{r mods_compare_scw16_candidate}
mods2compare <- c(reference_model, candidate_model)
h1_mod_cap <- "from the h1_1.14 reference model to the h1_2.00 SCW16 candidate model."
h2_mod_cap <- "from the h2_1.14 reference model to the h2_2.00 SCW16 candidate model."
```

## Single-stock hypothesis

::: {.panel-tabset}
### Biomass
```{r scw16_candidate_h1_biomass, fig.cap=paste0("Plot comparing biomass estimates ", h1_mod_cap)}
h1_candidate_ready <- all(model_file_status(geth(mods2compare, "h1"))$report_file)
if (h1_candidate_ready) {
  hyp <- "h1"
  res <- compareModels(geth(mods2compare, "h1"))
  plot(res, combine = TRUE, what = "biomass", stack = FALSE, main = "Biomass")
} else {
  message("Single-stock candidate comparison pending: h1_2.00 results are not available.")
}
```

### Recruitment
```{r scw16_candidate_h1_recruitment, fig.cap=paste0("Plot comparing recruitment estimates ", h1_mod_cap)}
if (h1_candidate_ready) {
  plot(res, combine = TRUE, what = "recruitment", stack = FALSE, main = "Recruitment")
}
```

### Fishing Mortality
```{r scw16_candidate_h1_fmort, fig.cap=paste0("Plot comparing fishing mortality estimates ", h1_mod_cap)}
if (h1_candidate_ready) {
  plot(res, combine = TRUE, what = "ftot", stack = FALSE, main = "Total Fishing Mortality")
}
```
:::

## Two-stock hypothesis

::: {.panel-tabset}
### Biomass
```{r scw16_candidate_h2_biomass, fig.cap=paste0("Plot comparing biomass estimates ", h2_mod_cap)}
h2_candidate_ready <- all(model_file_status(geth(mods2compare, "h2"))$report_file)
if (h2_candidate_ready) {
  hyp <- "h2"
  res <- compareModels(geth(mods2compare, "h2"))
  plot(res, combine = TRUE, what = "biomass", stack = FALSE, main = "Biomass")
} else {
  message("Two-stock candidate comparison pending: h2_2.00 results are not available.")
}
```

### Recruitment
```{r scw16_candidate_h2_recruitment, fig.cap=paste0("Plot comparing recruitment estimates ", h2_mod_cap)}
if (h2_candidate_ready) {
  plot(res, combine = TRUE, what = "recruitment", stack = FALSE, main = "Recruitment")
}
```

### Fishing Mortality
```{r scw16_candidate_h2_fmort, fig.cap=paste0("Plot comparing fishing mortality estimates ", h2_mod_cap)}
if (h2_candidate_ready) {
  plot(res, combine = TRUE, what = "ftot", stack = FALSE, main = "Total Fishing Mortality")
}
```
:::


# Notes

This working report is currently scoped to `h1_1.14.ctl` and `h2_1.14.ctl` as the reference pair, the fitted `0.01` through `0.05` data-replacement runs, and the `h1_2.00` and `h2_2.00` candidate pair as files and model outputs become available. Additional diagnostic and sensitivity sections can be added back once the benchmark sequence is settled.
