---
title: "ADMB vs RTMB Parity Check — JJM h1_1.14"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    self-contained: true
---

## Purpose

Confirm that the RTMB scaffold (`jjm_rtmb.R`) produces the same population
dynamics, observation predictions, and likelihood components as the ADMB
executable when seeded with the converged ADMB `.par` file for the `h1_1.14`
model configuration.

The comparison is *not* an optimization parity test — it is a parameter-fixed
forward-pass check. Both engines receive identical parameter values; any
residual differences indicate a coding discrepancy in the RTMB translation.

### RTMB entry points used here

| Function | Source | Role |
|---|---|---|
| `read_jjm(ctl)` | `read_jjm.R` | Parse `.dat` + `.ctl` into a structured list |
| `read_jjm_par(par, d)` | `read_par.R` | Load ADMB `.par` into the RTMB parameter list |
| `jjm_run(p, d)` | `jjm_rtmb.R` | Plain-R forward pass; returns all model quantities |

---

## Setup

```{r setup}
#| message: false
#| warning: false

suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(knitr)
})

# Paths relative to rtmb_jjm/ (where this .qmd lives)
ctl_file <- "../assessment/config/h1_1.14.ctl"
par_file <- "../assessment/results/h1_1.14.par"
rep_base <- "../assessment/results/h1_1.14"

source("read_jjm.R")
source("read_par.R")
source("jjm_rtmb.R")
source("../assessment/R/read-admb.R")
```

---

## Load ADMB baseline

```{r load-admb}
admb <- read_admb(rep_base)

# Pull the named NLL components from .rep
admb_nll_names <- c(
  "catch_like", "age_like_fsh", "length_like_fsh", "sel_like_fsh",
  "ind_like", "age_like_ind", "length_like_ind", "sel_like_ind",
  "rec_like", "fpen", "post_priors_indq", "post_priors"
)
admb_nll <- sapply(admb_nll_names, function(nm) {
  v <- admb[[nm]]
  if (is.null(v)) NA_real_ else as.numeric(v)
})

cat("ADMB total NLL:", admb$fit$nlogl, "\n")
cat("ADMB max gradient:", admb$fit$maxgrad, "\n")
```

---

## Load RTMB and run forward pass

```{r load-rtmb}
d   <- read_jjm(ctl_file)
p   <- read_jjm_par(par_file, d)
rep <- jjm_run(p, d)

cat("RTMB total NLL (implemented components):", rep$nll, "\n")
```

---

## NLL component comparison

The RTMB implementation currently covers all components **except** fishery
length compositions, which account for 471 / 1324 (36%) of the ADMB total.

```{r nll-table}
# Map RTMB component names to ADMB names for alignment
rtmb_mapped <- c(
  catch_like      = rep$nll_components["catch_like"],
  age_like_fsh    = rep$nll_components["age_like_fsh"],
  length_like_fsh = NA_real_,                            # not yet implemented
  sel_like_fsh    = rep$nll_components["sel_like_fsh"],
  ind_like        = rep$nll_components["ind_like"],
  age_like_ind    = rep$nll_components["age_like_ind"],
  length_like_ind = NA_real_,                            # not in h1_1.14 data
  sel_like_ind    = rep$nll_components["sel_like_ind"],
  rec_like        = rep$nll_components["rec_like"] +
                    rep$nll_components["rec_like_dev"],
  fpen            = rep$nll_components["fpen"],
  post_priors_indq = rep$nll_components["priors_indq"],
  post_priors     = rep$nll_components["prior_M"] +
                    rep$nll_components["prior_h"] +
                    rep$nll_components["prior_sigmar"]
)

nll_df <- tibble(
  component  = admb_nll_names,
  ADMB       = admb_nll,
  RTMB       = as.numeric(rtmb_mapped),
  diff       = RTMB - ADMB,
  implemented = !is.na(RTMB)
)

kable(nll_df, digits = 4,
      caption = "NLL components: ADMB (converged .par) vs RTMB forward pass")
```

```{r nll-summary}
implemented <- nll_df |> filter(implemented)
cat("Sum of implemented RTMB components:", sum(implemented$RTMB, na.rm=TRUE), "\n")
cat("Corresponding ADMB sum:            ", sum(implemented$ADMB, na.rm=TRUE), "\n")
cat("Residual difference:               ",
    sum(implemented$RTMB, na.rm=TRUE) - sum(implemented$ADMB, na.rm=TRUE), "\n")
```

---

## Catch predictions

```{r catch-pred}
dat  <- d$dat
yrs  <- seq(dat$styr, dat$endyr)
nfsh <- dat$nfsh

# ADMB pred_catch is in the .rep as "Predicted_catch" or similar;
# use the RTMB values against observed as a sanity check
obs_catch <- dat$catch_bio   # [nfsh × nyrs]

catch_df <- lapply(seq_len(nfsh), function(k) {
  tibble(
    year   = yrs,
    fleet  = paste0("F", k),
    obs    = obs_catch[k, ],
    rtmb   = rep$pred_catch[k, ]
  )
}) |> bind_rows()

ggplot(catch_df |> filter(obs > 0), aes(x = year)) +
  geom_point(aes(y = obs), shape = 1, size = 1.5) +
  geom_line(aes(y = rtmb), colour = "steelblue") +
  facet_wrap(~ fleet, scales = "free_y", ncol = 2) +
  labs(title = "Catch: observed (points) vs RTMB predicted (line)",
       y = "Catch (kt)", x = NULL) +
  theme_bw()
```

---

## Survey index predictions

```{r index-pred}
nind <- dat$nind

ind_df <- lapply(seq_len(nind), function(k) {
  yrs_k <- dat$yrs_ind[[k]]
  obs_k <- dat$obs_ind[[k]]
  pred_k <- rep$pred_ind[[k]]
  tibble(
    year  = yrs_k,
    index = paste0("I", k),
    obs   = obs_k,
    rtmb  = pred_k
  )
}) |> bind_rows()

ggplot(ind_df, aes(x = year)) +
  geom_point(aes(y = obs), shape = 1, size = 1.5) +
  geom_line(aes(y = rtmb), colour = "darkorange") +
  facet_wrap(~ index, scales = "free_y", ncol = 2) +
  labs(title = "Survey index: observed (points) vs RTMB predicted (line)",
       y = "Index", x = NULL) +
  theme_bw()
```

---

## Spawning biomass

```{r sp-biom}
# ADMB Sp_Biom from .rep
admb_spb_raw <- admb[["Sp_Biom"]]   # read_rep returns numeric matrix or vector

sp_df <- tibble(year = yrs, rtmb = rep$Sp_Biom)

if (!is.null(admb_spb_raw)) {
  # Sp_Biom in .rep is a single-row or vector of nyrs values
  admb_spb <- as.numeric(admb_spb_raw)
  if (length(admb_spb) == length(yrs)) {
    sp_df$admb <- admb_spb
  }
}

if ("admb" %in% names(sp_df)) {
  sp_df_long <- sp_df |>
    pivot_longer(c(rtmb, admb), names_to = "source", values_to = "Sp_Biom")
  ggplot(sp_df_long, aes(x = year, y = Sp_Biom, colour = source, linetype = source)) +
    geom_line(linewidth = 0.9) +
    scale_colour_manual(values = c(admb = "black", rtmb = "steelblue")) +
    labs(title = "Spawning biomass: ADMB vs RTMB", y = "SSB (kt)", x = NULL) +
    theme_bw()
} else {
  ggplot(sp_df, aes(x = year, y = rtmb)) +
    geom_line(colour = "steelblue") +
    labs(title = "Spawning biomass (RTMB)", y = "SSB (kt)", x = NULL) +
    theme_bw()
}
```

---

## Numbers at age — spot check

Compare RTMB `natage` to ADMB for a few key years. ADMB reports natage in the
`.rep` as `"Estimated numbers of fish"`.

```{r natage-check}
admb_natage_raw <- admb[["Estimated_numbers_of_fish"]]

spot_years <- c(1970, 1990, 2010, dat$endyr)
spot_idx   <- spot_years - dat$styr + 1L

rtmb_natage_spot <- rep$natage[spot_idx, ]
rownames(rtmb_natage_spot) <- as.character(spot_years)
colnames(rtmb_natage_spot) <- paste0("age", seq_len(dat$nages))

kable(round(rtmb_natage_spot, 1),
      caption = "RTMB numbers at age (spot years)")

if (!is.null(admb_natage_raw)) {
  # read_rep stores this as a matrix; rows = years, values are space-separated
  # The .rep line format: "  Year: YYYY  n1 n2 ... n12"
  # read_rep strips the non-numeric Year: label so it may misparse — skip if messy
  cat("ADMB natage matrix dimensions:", dim(admb_natage_raw), "\n")
}
```

---

## Selectivity — fishery 1, first and last blocks

```{r sel-fsh1}
sel1 <- rep$sel_fsh[[1L]]   # [nyrs × nages]
ages <- seq_len(dat$nages)

sel_df <- bind_rows(
  tibble(year = dat$styr, age = ages, sel = sel1[1L, ],  block = "first"),
  tibble(year = dat$endyr, age = ages, sel = sel1[dat$nyrs, ], block = "last")
)

ggplot(sel_df, aes(x = age, y = sel, colour = block)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2) +
  labs(title = "Fishery 1 selectivity — first vs last year",
       y = "Selectivity", x = "Age") +
  theme_bw()
```

---

## Implementation status

```{r status-table}
status <- tribble(
  ~Component,               ~Status,          ~Note,
  "read_jjm (dat + ctl)",   "complete",        "All h1_1.14 fields parsed",
  "read_jjm_par",           "complete",        "byrow fixes applied",
  "Natural mortality (M)",  "complete",        "Constant scalar; M_rw and Mage_offset TODO",
  "Selectivity type 1",     "complete",        "Age-specific, time-varying blocks",
  "Selectivity type 2",     "not implemented", "Single logistic",
  "Selectivity type 3",     "not implemented", "Double logistic",
  "Baranov catch eq.",      "complete",        "",
  "Bzero / initial N",      "complete",        "",
  "Numbers at age",         "complete",        "",
  "BH stock-recruit",       "complete",        "",
  "Survey predictions (q)", "complete",        "RW-q implemented",
  "Fishery age comps",      "complete",        "",
  "Survey age comps",       "complete",        "",
  "Fishery length comps",   "not implemented", "471/1324 NLL = 36% of total",
  "Survey length comps",    "n/a",             "No length data for any index in h1_1.14",
  "Catch likelihood",       "complete",        "",
  "Index likelihood",       "complete",        "",
  "Age comp likelihood",    "complete",        "Multinomial, fsh + ind",
  "Length comp likelihood", "not implemented", "Requires Get_Age2length ALK",
  "Rec likelihood",         "complete",        "",
  "Sel penalties",          "complete",        "Curvature, smoothness, descent",
  "Priors (q, M, h, sigR)", "complete",        "",
  "F penalty",              "complete",        "",
  "Rzero penalty",          "complete",        "",
  "get_msy / ref points",   "not implemented", "Post-estimation only",
  "Future projections",     "not implemented", "Post-estimation only"
)

kable(status, caption = "RTMB implementation status for h1_1.14")
```

---

## Session info

```{r session}
sessionInfo()
system("git -C .. rev-parse --short HEAD 2>/dev/null || echo 'no git'", intern = TRUE)
```
