---
output: 
  word_document:
    reference_docx:  report_template_v1.7.dotx
---

```{r setup, include=FALSE}

# ==================================================================
# SPRFMO Catch template reader (SC8 2020)
#
# 11/10/2019: first coding
# 03/10/2020: finalized coding for 2019 and 2020 data
# 04/10/2020: also available for earlier data now
# 05/10/2020: uploaded to jjm github
# ==================================================================

# Reset lists
# rm(list=ls())

# general libraries
library(readxl)        # excel reader from hadley; much quicker than the java based excel readers
library(lubridate)     # data and time functions
library(stringr)       # string manipulation
library(pander)        # for tables
library(reshape2)      # cast and melt dataframes
library(scales)        # pretty scales
library(tidyverse)     # data manipulation and piping

# source utilities
source("my utils.R")

# 2017
# data_path <- "D:/Dropbox/jurel/archiv/SC06_2018/Assessment data for CJM/ALK2017"
# fn        <- "ALK data 2017 SC6.RData"

# 2018
# data_path <- "D:/Dropbox/jurel/SC07_2019/Assessment data for CJM/ALK2018"
# fn        <- "ALK data 2018 SC7.RData"

# 2019
data_path <- file.path("C:/Users/Martin Pastoors/PFA/SPRFMO SC8 - Documents/Jack Mackerel/04 Data/ALK2019")
fn        <- "ALK data 2019 SC8.RData"

# Create file list for import 
file.list   <- c(
  list.files(path = data_path,recursive  = FALSE,pattern = "xls",full.names = TRUE,ignore.case= TRUE) )
# file.list   <- c(
#   list.files(path = "C:/Users/Martin Pastoors/PFA/SPRFMO SC8 - Documents/Jack Mackerel/04 Data/ALK2019",
#              recursive  = FALSE,pattern = "xls",full.names = TRUE,ignore.case= TRUE),
#   list.files(path = "C:/Users/Martin Pastoors/PFA/SPRFMO SC8 - Documents/Jack Mackerel/04 Data/ALK2019",
#              recursive  = FALSE,pattern = "xls",full.names = TRUE,ignore.case= TRUE) )
file.list <- file.list[!grepl("\\~",file.list)]


# read_catch function -------------------------------------------------------------------
# i <- 5
# ws<-"catch data"

read_catch <- function(file, ws, member, species, year) {
  
  t1 <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "B12:M13")) %>% 
    t() %>% 
    data.frame(stringsAsFactors = FALSE) %>%
    setNames(c("quarter", "year")) %>% 
    mutate(quarter = as.numeric(stringr::str_match_all(quarter, "[0-9]+")) ) %>%
    zoo::na.locf(.)                       # fill the empty values with previous values
  
  t <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "B15:M20", .name_repair = "minimal")) %>% 
    t() %>% 
    data.frame(stringsAsFactors = FALSE) %>% 
    setNames(c("variable","unit","F1","F2","F3","F4")) %>%
    bind_cols(t1) %>% 
    gather(key=fleet, value=value, 3:6) %>% 
    filter(!is.na(value)) %>% 
    mutate(unit = gsub("[[:punct:]]", "", tolower(unit))) %>% 
    mutate(variable = tolower(variable)) %>% 
    mutate(member=member, species=species, year=as.integer(year), file=basename(file))  %>% 
    mutate(value = as.numeric(value))
  

  # generate dataframe is not all empty
  if (nrow(t) > 0) {
    print(ws)
    return(t)
  }
  
} # end of function

# i <- 1
# ws = "sampling"
# file = file.list[i]

# read_sampling function -------------------------------------------------------------------

read_sampling <- function(file, ws, member, species, year) {
  
  t1 <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "B8:Q8")) %>% 
    t() %>% 
    data.frame(stringsAsFactors = FALSE) %>%
    setNames(c("quarter")) %>%
    mutate(quarter = as.numeric(stringr::str_match_all(quarter, "[0-9]+")),
           quarter = ifelse(quarter > 4, NA, quarter),
           year    = year) %>%
    zoo::na.locf(.)                        # fill the empty values with previous values

  t <- 
    read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "B9:Q14", .name_repair = "minimal") %>% 
    t() %>% 
    data.frame(stringsAsFactors = FALSE) %>% 
    setNames(c("variable","unit","F1","F2","F3","F4")) %>%
    bind_cols(t1) %>% 
    gather(key=fleet, value=value, 3:6) %>% 
    mutate(unit = gsub("[[:punct:]]", "", tolower(unit))) %>% 
    mutate(member=member, species=species, year=year, file=basename(file))  %>% 
    filter(!is.na(value)) %>% 
    mutate(value = as.numeric(value))
  
  # generate dataframe is not all empty
  if (nrow(t) > 0) {
    print(ws)
    return(t)
  }
  
} # end of function

# read_length function -------------------------------------------------------------------

read_length <- function(file, ws, member, species, year) {
  
  # fleet      <- gsub("LEN ","", ws)
  fleet      <- stringr::word(ws, 2)
  lengthtype <- as.character(read_excel(file, sheet = ws, col_names = FALSE, col_types = "text", range = "A8", .name_repair = "minimal"))
  lengthunit <- as.character(read_excel(file, sheet = ws, col_names = FALSE, col_types = "text", range = "A9", .name_repair = "minimal"))
  unit       <- as.character(read_excel(file, sheet = ws, col_names = FALSE, col_types = "text", range = "F5", .name_repair = "minimal"))

  t <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "A10:E109", .name_repair = "minimal")) %>% 
    setNames(c("length","quarter1","quarter2","quarter3","quarter4")) %>%
    gather(key=quarter, value=value, quarter1:quarter4) %>% 
    mutate(member=member, species=species, year=year, file=basename(file), fleet=fleet, unit=unit,
           lengthtype=lengthtype, lengthunit = lengthunit)  %>% 
    mutate(quarter = as.numeric(stringr::str_match_all(quarter, "[0-9]+")) ) %>%
    mutate(value   = as.numeric(gsub("\\s+", "", value) )) %>% 
    mutate(length  = as.numeric(length)) %>% 
    mutate(unit = gsub("[[:punct:]]", "", tolower(unit))) %>% 
    mutate(lengthunit = gsub("[[:punct:]]", "", tolower(lengthunit))) %>% 
    filter(!is.na(value)) %>% 
    
    mutate(value = ifelse(unit == "individuals", value/1000, value),
           unit  = ifelse(unit == "individuals", "thousands", unit)) %>% 
    mutate(value = ifelse(unit == "millions", value*1000, value),
           unit  = ifelse(unit == "millions", "thousands", unit)) %>%
    
    group_by(member, fleet, species, year, quarter, lengthtype) %>% 
    arrange(member, fleet, species, year, quarter, lengthtype, length) %>% 
    mutate(prop = value / sum(value)) %>% 
    mutate(cumvalue = cumsum(value),
           cumprop = cumsum(prop)) %>% 
    ungroup()
  
  
  # generate dataframe is not all empty
  if (nrow(t) > 0) {
    print(ws)
    return(t)
  }
  
} # end of function


# read_alk function -------------------------------------------------------------------

# file       <- file.list[1]
# worksheets <- excel_sheets(file)
# ws         <- worksheets[grepl("ALK", worksheets)][1]
# member     <- as.character(read_excel(file, sheet = 1, col_names = FALSE, col_types = "text", range = "F6"))
# species    <- as.character(read_excel(file, sheet = 1, col_names = FALSE, col_types = "text", range = "F5"))
# year       <- as.integer  (read_excel(file, sheet = 1, col_names = FALSE, col_types = "numeric", range = "K3"))
# i <- 3
# ws = "ALK F2"
# file = file.list[i]

read_alk <- function(file, ws, member, species, year) {
  
  # fleet      <- gsub("ALK ","", ws)
  fleet      <- stringr::word(ws, 2)
  lengthtype <- as.character(read_excel(file, sheet = ws, col_names = FALSE, col_types = "text", range = "A10", .name_repair = "minimal") )
  lengthunit <- as.character(read_excel(file, sheet = ws, col_names = FALSE, col_types = "text", range = "A11", .name_repair = "minimal") )

  # ages
  a <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, col_types = "text", range = "B11:N11"))  %>% 
    mutate_all( ~ paste0("age",.)) %>% 
    as.character() 
  
  t1 <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "A12:N111", .name_repair = "minimal")) %>% 
    setNames(c("length",all_of(a))) %>%
    mutate(quarter=1) %>% 
    gather(key=age, value=value, all_of(a)) %>% 
    filter(!is.na(value)) %>% 
    mutate(value   = as.numeric(gsub("\\s+", "", value) )) 
  
  t2 <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "P12:AC111", .name_repair = "minimal")) %>% 
    setNames(c("length",all_of(a))) %>%
    mutate(quarter=2) %>% 
    gather(key=age, value=value, all_of(a)) %>% 
    filter(!is.na(value)) %>% 
    mutate(value   = as.numeric(gsub("\\s+", "", value) )) 
  
  t3 <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "AE12:AR111", .name_repair = "minimal")) %>% 
    setNames(c("length",all_of(a))) %>%
    mutate(quarter=3) %>% 
    gather(key=age, value=value, all_of(a)) %>% 
    filter(!is.na(value)) %>% 
    mutate(value   = as.numeric(gsub("\\s+", "", value) )) 
  
  t4 <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "AT12:BG111", .name_repair = "minimal")) %>% 
    setNames(c("length",all_of(a))) %>%
    mutate(quarter=4) %>% 
    gather(key=age, value=value, all_of(a)) %>% 
    filter(!is.na(value)) %>% 
    mutate(value   = as.numeric(gsub("\\s+", "", value) )) 

  t <-
    bind_rows(t1, t2, t3, t4) %>% 
    mutate(member=member, species=species, year=year, file=basename(file), fleet=fleet,
           lengthtype=lengthtype, lengthunit = lengthunit)  %>% 
    mutate(value   = as.numeric(gsub("\\s+", "", value) )) %>% 
    mutate(length  = as.numeric(length)) %>% 
    mutate(age     = as.integer(gsub("age","",age))) %>% 
    mutate(lengthunit = gsub("[[:punct:]]", "", tolower(lengthunit))) %>% 
    group_by(member, fleet, species, year, quarter, length) %>% 
    mutate(prop = value / sum(value)) %>% 
    ungroup()
    

  # generate dataframe is not all empty
  if (nrow(t) > 0) {
    
    print(ws)
    return(t)
  }
  
} # end of function


# read_canum function -------------------------------------------------------------------

# ws <- "CN F1"

read_canum <- function(file, ws, member, species, year) {
  
  # fleet      <- gsub("CN ","", ws)
  fleet      <- stringr::word(ws, 2)
  unit       <- as.character(read_excel(file, sheet = ws, col_names = FALSE, col_types = "text", range = "C11:N11", .name_repair = "minimal") )
  
  t <- 
    suppressMessages(read_excel(file, sheet = ws, col_names = FALSE, na="NA", col_types = "text", range = "B12:N24", .name_repair = "minimal")) %>% 
    setNames(c("age","canum_1","meanlength_1","meanweight_1","canum_2","meanlength_2","meanweight_2",
                     "canum_3","meanlength_3","meanweight_3","canum_4","meanlength_4","meanweight_4")) %>%
    mutate(age = as.integer(gsub("\\+","",age))) %>% 
    pivot_longer(names_to = "tosplit", values_to="value", canum_1:meanweight_4) %>%
    mutate(unit=rep(unit,13)) %>% 
    separate(tosplit, into=c("variable","quarter"), sep="_") %>% 
    filter(!is.na(value)) %>% 
    mutate(unit = gsub("[[:punct:]]", "", tolower(unit))) %>% 
    mutate(member=member, species=species, year=year, file=basename(file), fleet=fleet)  %>% 
    mutate(value   = as.numeric(gsub("\\s+", "", value) )) %>% 
    
    mutate(value = ifelse(unit == "individuals", value/1000, value),
           unit  = ifelse(unit == "individuals", "thousands", unit)) %>% 
    mutate(value = ifelse(unit == "millions", value*1000, value),
           unit  = ifelse(unit == "millions", "thousands", unit)) %>%
    
    arrange(variable, quarter, age) %>% 
    ungroup()
  
  
  # generate dataframe is not all empty
  if (nrow(t) > 0) {
    
    print(ws)
    return(t)
  }
  
} # end of function




# create empty dataframes
catch <- sampling <- length <- alk <- canum <- data.frame(stringsAsFactors = FALSE)

i    <- 3
file <- file.list[i]
# ws   <- "catch data"

# start file reading loop
for (i in 1:length(file.list)){                                           

  
  # get name and number of worksheets in the file
  file        <- file.list[i]
  worksheets  <- excel_sheets(file)
  nworksheets <- length(worksheets)
  
  print(paste(i, basename(file), sep=" "))
  
  # generic information
  member <- as.character(read_excel(file, sheet = "START HERE", col_names = FALSE, col_types = "text", range = "F6", .name_repair = "minimal"))
  species<- as.character(read_excel(file, sheet = "START HERE", col_names = FALSE, col_types = "text", range = "F5", .name_repair = "minimal"))
  year   <- as.integer  (read_excel(file, sheet = "START HERE", col_names = FALSE, col_types = "numeric", range = "K3", .name_repair = "minimal"))
  
  # catch
  for (ws in worksheets[grepl("catch", worksheets)]) {
    catch <- bind_rows(catch, read_catch(file=file, ws=ws, member=member, species=species, year=year)) }
  
  # sampling
  for (ws in worksheets[grepl("sampling", worksheets)]) {
    sampling <- bind_rows(sampling, read_sampling(file=file, ws=ws, member=member, species=species, year=year)) }

  # length
  for (ws in worksheets[grepl("LEN", worksheets)]) {
    length <- bind_rows(length, read_length(file=file, ws=ws, member=member, species=species, year=year)) }

  # alk
  for (ws in worksheets[grepl("ALK", worksheets)]) {
    alk <- bind_rows(alk, read_alk(file=file, ws=ws, member=member, species=species, year=year)) }
  
  # canum
  for (ws in worksheets[grepl("CN", worksheets)]) {
    canum <- bind_rows(canum, read_canum(file=file, ws=ws, member=member, species=species, year=year)) }
  
} # end of i loop

# save(catch, sampling, length, alk, canum, file=file.path("D:/TEMP",fn))
save(catch, sampling, length, alk, canum, file=file.path("D:/TEMP",fn))

```

8th MEETING OF THE SCIENTIFIC COMMITTEE

**Catch template reader.rmd**

Corresponding author: mpastoors@pelagicfish.eu

`r format(Sys.time(), '%d/%m/%Y')`

Overview of catch templates 2019 through automated reading and processing

Files read

```{r echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE}

print(basename(file.list))

```

Catch by quarter

```{r echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE}

# plot catch
catch %>%
  mutate(value=as.numeric(value)) %>% 
  mutate(quarter = paste0("Q", quarter)) %>% 
  mutate(yearquarter = paste0(year, quarter)) %>% 
  
  ggplot(aes(x=yearquarter, y=value, group=member)) + 
  theme_publication() +
  theme(panel.spacing     = unit(2, "mm"),
        legend.key.width  = unit(1, "cm"),
        legend.title      = element_blank(),
        panel.grid.minor  = element_blank(),
        # legend.position = "null",
        text              = element_text(size=12) ) +
  
  labs(x = "quarter", y = "catch") +
  
  geom_bar(aes(fill=member), stat="identity", alpha=1) +
  facet_grid(fleet~.)
# facet_grid(.~quarter)

```

##### page break

Number of length measurements

```{r echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE}

# plot sampled ages
sampling %>%
  filter(variable=="measured") %>% 
  mutate(value=as.numeric(value)) %>% 
  mutate(quarter = paste0("Q", quarter)) %>% 
  mutate(yearquarter = paste0(year, quarter)) %>% 
  
  ggplot(aes(x=yearquarter, y=value, group=member)) + 
  theme_publication() +
  theme(panel.spacing     = unit(2, "mm"),
        legend.key.width  = unit(1, "cm"),
        legend.title      = element_blank(),
        panel.grid.minor  = element_blank(),
        # legend.position = "null",
        text              = element_text(size=12) ) +
  
  labs(x = "quarter", y = "catch") +
  
  geom_bar(aes(fill=member), stat="identity", alpha=1) +
  facet_grid(fleet~.)
# facet_grid(.~quarter)

```

##### page break

Number of age measurements

```{r echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE}

# plot sampled ages
sampling %>%
  filter(variable=="aged") %>% 
  mutate(value=as.numeric(value)) %>% 
  mutate(quarter = paste0("Q", quarter)) %>% 
  mutate(yearquarter = paste0(year, quarter)) %>% 
  
  ggplot(aes(x=yearquarter, y=value, group=member)) + 
  theme_publication() +
  theme(panel.spacing     = unit(2, "mm"),
        legend.key.width  = unit(1, "cm"),
        legend.title      = element_blank(),
        panel.grid.minor  = element_blank(),
        # legend.position = "null",
        text              = element_text(size=12) ) +
  
  labs(x = "quarter", y = "catch") +
  
  geom_bar(aes(fill=member), stat="identity", alpha=1) +
  facet_grid(fleet~.)
# facet_grid(.~quarter)

```

##### page break


Cumulative length proportions 

```{r echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE}

# plot cumulative proportions at length
length %>%   
  filter(tolower(lengthtype) == "fork length") %>% 
  mutate(quarter = paste0("Q", quarter)) %>% 
  mutate(yearquarter = paste0(year, quarter)) %>% 
  
  ggplot(aes(x=length, y=cumprop, group=member)) + 
  theme_publication() +
  theme(panel.spacing     = unit(2, "mm"),
        legend.key.width  = unit(1, "cm"),
        legend.title      = element_blank(),
        panel.grid.minor  = element_blank(),
        # legend.position = "null",
        text              = element_text(size=12) ) +
  
  labs(x = "length", y = "prop") +
  
  geom_line(aes(colour=member, group=member), alpha=1) +
  facet_grid(fleet~yearquarter)
  # facet_grid(.~quarter)

```

##### page break

ALK

```{r echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE}

# plot age-length keys
alk %>%   
  # filter(year == 2019) %>% 
  mutate(quarter = paste0("Q", quarter)) %>% 
  mutate(yearquarter = paste0(year, quarter)) %>% 
  
  ggplot(aes(x=length, y=age, group=quarter)) + 
  theme_publication() +
  theme(panel.spacing     = unit(2, "mm"),
        legend.key.width  = unit(1, "cm"),
        legend.title      = element_blank(),
        panel.grid.minor  = element_blank(),
        # legend.position = "null",
        text              = element_text(size=12) ) +
  
  labs(x = "length", y = "age") +
  
  geom_point(aes(size=prop, colour=member), alpha=0.5) +
  # facet_grid(fleet~quarter)
  facet_grid(year~quarter)

```

##### page break

CANUM

```{r echo=FALSE, fig.asp=1.0, fig.align="center", message=FALSE, warning=FALSE}

# plot canum
canum %>%   
  # filter(year == myyear) %>%
  filter(variable == "canum") %>% 
  mutate(quarter = paste0("Q", quarter)) %>% 
  mutate(yearquarter = paste0(year, quarter)) %>% 
  
  ggplot(aes(x=age, y=value, group=member)) + 
  theme_publication() +
  theme(panel.spacing     = unit(2, "mm"),
        legend.key.width  = unit(1, "cm"),
        legend.title      = element_blank(),
        panel.grid.minor  = element_blank(),
        # legend.position = "null",
        text              = element_text(size=12) ) +
  
  labs(x = "age", y = "canum") +
  
  geom_bar(aes(fill=member, group=member), stat="identity", alpha=1) +
  facet_grid(fleet~yearquarter)
# facet_grid(.~quarter)





```

##### page break

