---
title: "Chilean age data explorations"
output:
  html_document:
    df_print: paged
---

This is an exploration of current data used in the assessment compared with new revisions provided by Chile

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r LoadData, echo=FALSE}

library(tidyverse)
library(ggplot2)
library(ggthemes)
library(patchwork)

options(dplyr.summarise.inform = FALSE)

knitr::opts_chunk$set(echo = FALSE,	message = FALSE,	warning = FALSE,	comment = "",	crop = TRUE )
knitr::opts_chunk$set(fig.width=10) 

# Read in new data 
df_age <- 
  read.csv("All_Age_Data_Chile.csv", header=TRUE, stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM") %>% 
  mutate(fleet = stringr::str_extract(Zone, "(\\d)+")) %>% 
  mutate(quarter = stringr::str_extract(Trimester, "(\\d)+"))
head(df_age)

# Read in data that is in the assessment model for same sources 
df_age_in <- 
  read.csv("AgeDataInAssessment.csv") %>% 
  setNames(c("Year","Fleet","type","Label",1:12)) %>% 
  pivot_longer(cols =5:16,names_to="age")

head(df_age_in)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# df_age %>% filter(Year>2010,grepl('Fleet 1',Zone)) %>% group_by(Method,Year) %>% mutate(Catch_tot=sum(Catch_no)) %>% ungroup() %>%
# group_by(Method,Year,Age) %>% summarise(Proportion=sum(Catch_no)/Catch_tot) %>%
# ggplot(aes(x=Age,y=Proportion,fill=Method,group=Year)) +
# geom_bar(stat='identity',position="dodge2") + theme_few() + facet_grid(Year~quarter)

plist <- list()

plist[[1]] <-
  df_age %>% 
  filter(Year>2010,grepl('Fleet 1',Zone)) %>% 
  
  ggplot(aes(x=Age,y=Proportion,fill=Method,group=Method)) +
  theme_few() + 
  theme(legend.position="none") +
  geom_bar(stat='identity',position = position_dodge2(width = 0.9, preserve = "single"), alpha=0.5) + 
  geom_line(aes(colour=Method), size=1) +
  labs(title="Fleet 1") +
  facet_grid(quarter~Year)

plist[[2]] <-
  df_age %>% 
  filter(Year>2010,grepl('Fleet 2',Zone)) %>% 
  
  ggplot(aes(x=Age,y=Proportion,fill=Method,group=Method)) +
  theme_few() + 
  theme(legend.position="bottom") +
  geom_bar(stat='identity',position = position_dodge2(width = 0.9, preserve = "single"), alpha=0.5) + 
  geom_line(aes(colour=Method), size=1) +
  labs(title="Fleet 2") +
  facet_grid(quarter~Year)

print(patchwork::wrap_plots(plist) + 
  patchwork::plot_layout(ncol = 1, heights = c(0.45, 0.55)) +
  patchwork::plot_annotation() & theme(plot.tag = element_text(size = 8)))

```

# Consistency check on age compositions
It is of interest to ensure that the data Chile provided for 2021 is the same (or nearly so) as that used in the current model. As such, we
extracted the data used for the 2020 Jack mackerel assessment into a dataframe to compare with the 2021 data submission using the "antiguo" method.
```{r Compare consistency,echo=FALSE}
# Read in data that is in the assessment model for same sources 
df_age_in <- read.csv("AgeDataInAssessment.csv") 

# Make a plot of currently used wt-at-age for S-C Chile
# 
names(df_age_in) <- c("Year","Fleet","type","Label",1:12)
df_age_in <- df_age_in %>% pivot_longer(cols =5:16,names_to="age")

plt_flt<- function(flt=1,firstyr=2000) {
  tmp1 <- df_age %>% filter(Year>firstyr,grepl(paste('Fleet',flt),Zone)) %>% 
  group_by(Method,Year,Age) %>% 
  summarise(Catch_no=sum(Catch_no) ) %>%
  group_by(Method,Year) %>% mutate(Proportion=Catch_no/sum(Catch_no)) 
tmp2 <- df_age_in %>% 
  filter(type=='catch',Year>firstyr,Fleet==flt) %>%  mutate(Age=as.integer(age)) %>% 
  group_by(Year,Age) %>% 
  transmute(Year,Method="assessment",Age,Catch_no=sum(value)) %>%
  group_by(Year) %>% mutate(Proportion=Catch_no/sum(Catch_no)) 

  rbind(tmp1,tmp2) %>% filter(Age %in% (1:8))  %>% filter(Method != "validacion") %>% mutate(Age=as.factor(Age)) %>% 
  ggplot(aes(x=Age,y=Proportion,fill=Method,group=Year)) +
  geom_bar(stat='identity',position="dodge2") + theme_few(base_size=11) + 
    ggtitle(paste("Fleet",flt)) +
  facet_grid(Year~Method) + theme(legend.position = "none") 
}
plt_flt(1)
plt_flt(2)



```



# Weight-at-age

```{r First wt-age view, echo=TRUE}
# Combine assessment w/ new file
# 
# Average wt age
tmp1 <- df_age %>% filter(Age<8,Year>2000,grepl('Fleet 2',Zone)) %>% group_by(Method,Year,Age) %>% 
  summarise(Age=as.factor(Age),Catch_wt=sum(Catch_wt),Catch_no=(sum(Catch_no)),awt=1e6*Catch_wt/Catch_no) %>% transmute(Year,Method,Age,awt)
tmp2 <- df_age_in %>% filter(as.numeric(age)<8,type=='wtage',Year>2000,Fleet==2) %>%  
  transmute(Year,Method="assessment",Age=as.factor(as.numeric(age)),awt=value*1000)

rbind(tmp1,tmp2) %>% 
  ggplot(aes(x=Year,y=awt,color=Age,shape=Method,type=Method)) + geom_point(size=2) + geom_line() + theme_few() +
  facet_grid(Method~.)

```

Now to focus in closer on some specific ages...

```{r}
rbind(tmp1,tmp2) %>% filter(Age %in% 2:4) %>%  mutate(Age=as.factor(Age)) %>% 
  ggplot(aes(x=Year,y=awt,color=Method,shape=Age,type=Age)) + geom_point(size=2) + geom_line() + theme_few() + ylab("Average wt (g)") #+ facet_grid(Method~.)
```
