---
title: "Chilean age data explorations"
output:
  html_document:
    df_print: paged
---

This is an exploration of current data used in the assessment compared with new revisions provided by Chile

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r LoadData, echo=FALSE}

library(tidyverse)
library(ggplot2)
library(ggthemes)
library(patchwork)

options(dplyr.summarise.inform = FALSE)

knitr::opts_chunk$set(echo = FALSE,	message = FALSE,	warning = FALSE,	comment = "",	crop = TRUE )
knitr::opts_chunk$set(fig.width=10) 

# Read in new data 
df_age <- 
  read.csv("All_Age_Data_Chile.csv", header=TRUE, stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM") %>% 
  mutate(fleet = stringr::str_extract(Zone, "(\\d)+")) %>% 
  mutate(quarter = stringr::str_extract(Trimester, "(\\d)+"))
head(df_age)

# Read in data that is in the assessment model for same sources 
df_age_in <- 
  read.csv("AgeDataInAssessment.csv") %>% 
  setNames(c("Year","Fleet","type","Label",1:12)) %>% 
  pivot_longer(cols =5:16,names_to="age")

head(df_age_in)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# df_age %>% filter(Year>2010,grepl('Fleet 1',Zone)) %>% group_by(Method,Year) %>% mutate(Catch_tot=sum(Catch_no)) %>% ungroup() %>%
# group_by(Method,Year,Age) %>% summarise(Proportion=sum(Catch_no)/Catch_tot) %>%
# ggplot(aes(x=Age,y=Proportion,fill=Method,group=Year)) +
# geom_bar(stat='identity',position="dodge2") + theme_few() + facet_grid(Year~quarter)

plist <- list()

plist[[1]] <-
  df_age %>% 
  filter(Year>2010,grepl('Fleet 1',Zone)) %>% 
  
  ggplot(aes(x=Age,y=Proportion,fill=Method,group=Method)) +
  theme_few() + 
  theme(legend.position="none") +
  geom_bar(stat='identity',position = position_dodge2(width = 0.9, preserve = "single"), alpha=0.5) + 
  geom_line(aes(colour=Method), size=1) +
  labs(title="Fleet 1") +
  facet_grid(quarter~Year)

plist[[2]] <-
  df_age %>% 
  filter(Year>2010,grepl('Fleet 2',Zone)) %>% 
  
  ggplot(aes(x=Age,y=Proportion,fill=Method,group=Method)) +
  theme_few() + 
  theme(legend.position="bottom") +
  geom_bar(stat='identity',position = position_dodge2(width = 0.9, preserve = "single"), alpha=0.5) + 
  geom_line(aes(colour=Method), size=1) +
  labs(title="Fleet 2") +
  facet_grid(quarter~Year)

print(patchwork::wrap_plots(plist) + 
  patchwork::plot_layout(ncol = 1, heights = c(0.45, 0.55)) +
  patchwork::plot_annotation() & theme(plot.tag = element_text(size = 8)))

```

# Weight-at-age

```{r First wt-age view, echo=TRUE}
# Combine assessment w/ new file
# 
# Average wt age
tmp1 <- df_age %>% filter(Age<8,Year>2010,grepl('Fleet 2',Zone)) %>% group_by(Method,Year,Age) %>% 
  summarise(Age=as.factor(Age),Catch_wt=sum(Catch_wt),Catch_no=(sum(Catch_no)),awt=1e6*Catch_wt/Catch_no) %>% transmute(Year,Method,Age,awt)
tmp2 <- df_age_in %>% filter(as.numeric(age)<8,type=='wtage',Year>2010,Fleet==2) %>%  
  transmute(Year,Method="assessment",Age=as.factor(as.numeric(age)),awt=value*1000)
rbind(tmp1,tmp2) %>% 
  ggplot(aes(x=Year,y=awt,color=Age,shape=Method,type=Method)) + geom_point(size=2) + geom_line() + theme_few() +
  facet_grid(Method~.)
```

Now to focus in closer on some specific ages...

```{r}
rbind(tmp1,tmp2) %>% filter(Age %in% 4:5) %>%  mutate(Age=as.factor(Age)) %>% 
  ggplot(aes(x=Year,y=awt,color=Method,shape=Age,type=Age)) + geom_point(size=2) + geom_line() + theme_few() #+ facet_grid(Method~.)
```
