---
title: "Jack Mackerel Assessment SC09"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir=here::here())
knitr::opts_chunk$set(warning=F, message=F, echo=F, results=F,fig.width=6, fig.height=5)
```

This document was compiled in `RMarkdown`, and shows the incremental results of the Chilean Jack Mackerel (*Trachurus murphyi*) stock assessment update in `r format(Sys.time(), "%Y")`. The files associated with this document can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

Annoted data files can be found in the Excel spreadsheet `JM Data files for SC09.xlsx` on [`jjm/assessment/data`](https://github.com/SPRFMO/jjm/tree/master/assessment/data).

The code to create the input files for this assessment and to run these models can be found in [`jjm/assessment/R/SC09_Bridging.R`](https://github.com/SPRFMO/jjm/tree/master/assessment/R/SC09_Bridging.R). Should you choose to run the models, please ensure that you have:

* Compiled the latest `jjm/src/jjms.tpl`
  - This can be done by navigating to the `jjm/src` folder in your Terminal, and using the `make` command
  - You will need to have [ADMB](http://www.admb-project.org/) installed to do this.
  - This does not need to be done if you're only re-compiling the R Markdown document.
* Updated the `jjmR` package
  - This can be done in `R` using the command `remotes::install_github("SPRFMO/jjmR")`


# Model Naming Convention
File naming conventions have been changed to reflect the stock structure hypotheses associated with each run. The `h1` denotes the single-stock hypothesis, while `h2` denotes the two-stock one.

Model | Description
------|--------------
**Models 0.x**| **Data introductions**
0.00     |  Exact 2020 (single stock `h1` and two-stock `h2`) model and data set through 2020 (mod1.0 from SC08)
0.01     |  As 0.00 but with revised catches through 2020 (currently still estimates)
0.02     |  As 0.01 but with updated 2020 fishery age composition data for N_Chile, SC_Chile, and Offshore_Trawl, and updated 2020 fishery length composition data for FarNorth
0.03     |  As 0.02 but with updated 2020 weight at age data for all fisheries and CPUE indices
0.04     |  As 0.03 but replaced offshore CPUE up to 2020
0.05     |  As 0.04 but with 2021 catch projections
0.06     |  As 0.05 but with updated 2021 fishery age composition data for N_Chile, SC_Chile, and Offshore_Trawl, and updated 2020 fishery length composition data for FarNorth
0.07     |  As 0.06 but but with updated 2021 weight at age data for N_Chile, SC_Chile, and FarNorth fleets, and for their associated CPUE indices
0.08     |  As 0.07 but replaced SC_Chile_CPUE index (traditional absolute scaled CPUE by trip)
0.09     |  As 0.08 but replaced Peru_CPUE index
0.10     |  As 0.09 but updated 2021 AcousticN_Survey index, with associated age composition and weight at age
-----------|--------------
**Models 1.x**| **(NOT RUN YET) Updated Model and Sensitivities**
1.00     | Update model (selectivity changes, recruitment) to 2021; 0.10 data file
1.01     | As 1.00 but use revised data series "antiguo" (assessment/NewAgeData/AgeDataInAssessment.csv)
1.02     | As 1.01 but incorporate revised (validated) age data for surveys and fleets with M and maturity updated (M=0.35)
1.03     | As 1.02 but M=0.45
1.04     | As 1.00 but with increased uncertainty for final year CPUE indices
-----------|--------------
**Models 1.x**| **For Benchmark**
1.01    |   Replace SC_Chile_CPUE with CPUE index by set


```{r install_packages, eval=F, cache=F, echo=T}
if(!'devtools' %in% installed.packages()) install.packages('devtools')
devtools::install_github("SPRFMO/jjmR")

if(!'kableExtra' %in% installed.packages()) install.packages('kableExtra')
```

You'll need to be in the `jjm/assessment` directory in order for the code here to run.

```{r pkgs, echo=T}
library(jjmR)
library(tidyverse)
library(kableExtra)

# MP note: normally I never use setwd in rmarkdown because it has unexpected behaviour. 
# I thought you would always end up in the jjm rootdirectory if you start up the markdown file?
# I cannot change the working directory by using setwd() ??
# LQ It might depend on the programme you use to open the file? Would be great if someone could test if this runs.

pwd <- getwd()
# if (!grepl(basename(pwd), "assessment", ignore.case = TRUE)) {
#   stop(paste("Set working directory to jjm/assessment"))
# }

geth <- function(mod,h=hyp) paste0(h,"_", mod)

fn.plotind <- function(mods2compare, indname) {
  fn.seldata <- function(x) {
  x$data$Index[,i] %>%
    bind_rows() %>%
    pivot_longer(everything(), names_to="year") %>%
    drop_na() %>%
    mutate(year=as.numeric(year),
            assessment_year=max(year))
  }

  mods <- compareModels(geth(mods2compare, "h1"))
  i <- grep(indname,mods[[1]]$data$Inames)
  dat2use <- list()
  for(m in 1:length(mods)) {
    dat2use[[m]] <- fn.seldata(mods[[m]])
  }

  p <- map_dfr(dat2use, ~as_tibble(.)) %>%
        mutate(assessment_year=as.factor(assessment_year)) %>%
        ggplot(aes(x=year,y=value,colour=assessment_year)) +
        geom_line() +
        theme_minimal() + 
        scale_x_continuous(breaks= scales::pretty_breaks())
  print(p)
}

```

# Re-running Last Year's Model (a sanity check)
Re-running the `r as.numeric(format(Sys.time(), "%Y"))-1` model and comparing the results with that year's SC meeting.


## Single-stock hypothesis {.tabset}
```{r load_prev_h1}
hyp <- "h1"

# mod0.00 <- runit(geth("0.00"),pdf=TRUE,portrait=F,est=TRUE,exec="../src/jjms")
mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

# mod_prev <- readJJM(geth("1.00"), path = "config", input = "input")
# save(mod_prev, file="results/mod_prev_h1.Rdat")

load("results/mod_prev_h1.Rdat")

```
### Biomass

```{r biomass_h1_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

oldnewMods <- combineModels(mod0.00,mod_prev)

plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h1_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```
## Two-stock hypothesis {.tabset}
```{r load_prev_h2}
# mod0.00 <- runit(geth("0.00"),pdf=TRUE,portrait=F,est=TRUE,exec="../src/jjms")
hyp <- "h2"
mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

load("results/mod_prev_h2.Rdat")

```

### Biomass

```{r biomass_h2_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

oldnewMods <- combineModels(mod0.00,mod_prev)

plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h2_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```


### Fishing Mortality
```{r fmort_h2_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Incremental Data Updates

The most updated table of model runs can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

## Updating last year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))-1` include catch estimates, age and length compositions, and indices of abundance. 

```{r}
mods2compare <- c("0.00","0.01","0.02","0.03", "0.04")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h1"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}

plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Two-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h2_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h2"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h2_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h2_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}

plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Updating this year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))` include projected catch estimates, age and length compositions, and indices of abundance. 

Currently, only the Chilean and Offshore CPUE indices have been made available (to me at least).

```{r}
mods2compare <- c("0.04","0.05","0.06","0.07", "0.08", "0.09", "0.10")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datcurr, fig.cap=paste0("Plot comparing biomass estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
hyp <- "h1"
Dat_Curr <- compareModels(geth(mods2compare))

plot(Dat_Curr,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datcurr, fig.cap=paste0("Plot comparing recruitment estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
plot(Dat_Curr,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datcurr, fig.cap=paste0("Plot comparing fishing mortality estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}

plot(Dat_Curr,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h2_datcurr, fig.cap=paste0("Plot comparing biomass estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
hyp <- "h2"
Dat_Curr <- compareModels(geth(mods2compare))

plot(Dat_Curr,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h2_datcurr, fig.cap=paste0("Plot comparing recruitment estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
plot(Dat_Curr,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h2_datcurr, fig.cap=paste0("Plot comparing fishing mortality estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}

plot(Dat_Curr,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Stepping through the CPUE replacements
### SC Chile CPUE
```{r, fig.height=3}
mods2compare <- c("0.07", "0.08")

fn.plotind(mods2compare, "Chile_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
Chile_CPUE <- compareModels(geth(mods2compare, "h1"))

plot(Chile_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Chile_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}

plot(Chile_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Chile_CPUE <- compareModels(geth(mods2compare))

plot(Chile_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Chile_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Chile_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Peru CPUE
```{r, fig.height=3}
mods2compare <- c("0.08", "0.09")

fn.plotind(mods2compare, "Peru_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h1"
Peru_CPUE <- compareModels(geth(mods2compare))

plot(Peru_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Peru_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}

plot(Peru_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Peru_CPUE <- compareModels(geth(mods2compare))

plot(Peru_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Peru_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Peru_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Offshore CPUE
```{r, fig.height=3}
mods2compare <- c("0.03", "0.04")

fn.plotind(mods2compare, "Offshore_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h1"
Offshore_CPUE <- compareModels(geth(mods2compare))

plot(Offshore_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Offshore_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Offshore_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Offshore_CPUE <- compareModels(geth(mods2compare))

plot(Offshore_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Offshore_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Offshore_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Final Data Update
This just shows the final data update, using the exact same model (i.e., with the same control files).

```{r}
mods2compare <- c("0.00","0.10")
```

## Single-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h1_datfin, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
hyp <- "h1"
Dat_Fin <- compareModels(geth(mods2compare))

plot(Dat_Fin,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h1_datfin, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
plot(Dat_Fin,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}

plot(Dat_Fin,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h2_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
hyp <- "h2"
Dat_Fin <- compareModels(geth(mods2compare))

plot(Dat_Fin,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h2_datfin, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
plot(Dat_Fin,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h2_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}

plot(Dat_Fin,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Model Update
These results are from updating the model to include selectivity changes in the most recent year, and to extend the recruitment regime shift time series. This was the same procedure that was applied to the previous year.

```{r}
mods2compare <- c("0.00","1.00")
```
## Single-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h1_base, fig.cap=paste0("Plot comparing biomass estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
hyp <- "h1"
Mod_Update <- compareModels(geth(mods2compare))

plot(Mod_Update,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h1_base, fig.cap=paste0("Plot comparing recruitment estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
plot(Mod_Update,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_base, fig.cap=paste0("Plot comparing fishing mortality estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}

plot(Mod_Update,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h2_base, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
hyp <- "h2"
Mod_Update <- compareModels(geth(mods2compare))

plot(Mod_Update,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h2_base, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
plot(Mod_Update,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h2_base, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model  (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}

plot(Mod_Update,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Likelihood Table
```{r results="asis"}
hyp <- "h1"
finMod <- "1.00"
h1 <- readJJM(geth(finMod), path = "config", input = "input")

hyp <- "h2"
h2 <- readJJM(geth(finMod), path = "config", input = "input")

LL <- cbind(summary(h1)$like,summary(h2)$like)

knitr::kable(LL) %>% kableExtra::kable_styling()
```

# Sensitivity Analyses

## Chile's Revised Age Data ("Antiguo")

* Updated age composition and weight at age for Chile_SC and Chile_N fleets, and also for AcousCS and AcousN surveys
* Sample sizes remained the same
* Current year is downweighted, as usual

* **The data for Chile_AcousCS include 2010, 2011, 2012, 2017, and 2020. But this index hasn't been updated since 2009- were we supposed to also be updating this? Should we ignore those years of data?**
* **In the antiguo dataset, summing up the capt_ton by year leads to numbers greater than historical total catch (~7 mil tons in 1995). Is there something we're missing?**


```{r}
mods2compare <- c("1.00","1.01")
```

## Single-stock hypothesis {.tabset}
### Biomass
```{r}
Antiguo <- compareModels(geth(mods2compare,"h1"))

plot(Antiguo,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r}
plot(Antiguo,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r }
plot(Antiguo,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r}
Antiguo <- compareModels(geth(mods2compare,"h2"))

plot(Antiguo,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r}
plot(Antiguo,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r}
plot(Antiguo,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Chile's New Age Data ("Validacion")
```{r}
mods2compare <- c("1.00","1.02")
```

## Single-stock hypothesis {.tabset}
### Biomass
```{r}
Validacion <- compareModels(geth(mods2compare,"h1"))

plot(Validacion,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r}
plot(Validacion,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r }
plot(Validacion,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r}
Validacion <- compareModels(geth(mods2compare,"h2"))

plot(Validacion,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r}
plot(Validacion,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r}
plot(Validacion,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Other Business
## General



## Other models to run
* Sensitivities to new age data as discussed in the data workshop
* Projection runs (recruitment regimes)
* Increase uncertainty for most recent year of CPUE for Chile, Offshore



