---
title: "Jack Mackerel Assessment SC09"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir=here::here())
knitr::opts_chunk$set(warning=F, message=F, echo=F, results=F,fig.width=6, fig.height=5)
```

This document was compiled in `RMarkdown`, and shows the incremental results of the Chilean Jack Mackerel (*Trachurus murphyi*) stock assessment update in `r format(Sys.time(), "%Y")`. The files associated with this document can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

Annoted data files can be found in the Excel spreadsheet `JM Data files for SC09.xlsx` on [`jjm/assessment/data`](https://github.com/SPRFMO/jjm/tree/master/assessment/data).

Currently, the files resulting from the model runs are not on the Github site, so this `.rmd` file cannot be recompiled without first running some code found in `jjm/assessment/R/SC08.R` to run all the models. Prior to doing this, please compile the latest `jjm/src/jjms.tpl`.


# Model Naming Convention
File naming conventions have been changed to reflect the stock structure hypotheses associated with each run. The `h1` denotes the single-stock hypothesis, while `h2` denotes the two-stock one.

Model | Description
------|--------------
**Models 0.x**| **Data introductions**
0.00     |  Exact 2020 (single stock `h1` and two-stock `h2`) model and data set through 2020 (mod1.0 from SC08)
0.01     |  As 0.00 but with revised catches through 2020 (currently still estimates)
0.02     |  As 0.01 but with updated 2020 fishery age composition data for N_Chile, SC_Chile, and Offshore_Trawl, and updated 2020 fishery length composition data for FarNorth
0.03     |  As 0.02 but with updated 2020 weight at age data for all fisheries and CPUE indices
0.04     |  As 0.03 but replaced offshore CPUE up to 2020
0.05     |  As 0.04 but with 2021 catch projections
0.06     |  As 0.05 but with updated 2021 fishery age composition data for N_Chile, SC_Chile, and Offshore_Trawl, and updated 2020 fishery length composition data for FarNorth
0.07     |  As 0.06 but but with updated 2021 weight at age data for all fisheries and CPUE indices
0.08     |  As 0.07 but replaced SC_Chile_CPUE index (traditional absolute scaled CPUE by trip)
-----------|--------------
**Models 1.x**| **(NOT RUN YET) Updated Model and Sensitivities**
1.00     |  Update model (selectivity changes, recruitment) to 2021; 0.xx data file
-----------|--------------
**Models 1.x**| **For Benchmark**
1.01    |   Replace SC_Chile_CPUE with CPUE index by set

Make sure that the `jjmR` package is updated with `devtools::install_github("SPRFMO/jjmR")`. `jjms` will need to be updated as well if you decide to run the models on your own.

## Questions
* Are these all the data updates we're expecting? Last year's update included Chile_AcousN index, Peru_CPUE
* Age composition data were provided for the FarNorth fleet - what do we do with them?
* Weight-at-age for FarNorth fleet is different for 2020 and 2021, when it's been the same from 2015-2019. Is that right?

```{r install_packages, eval=F, cache=F, echo=T}
if(!'devtools' %in% installed.packages()) install.packages('devtools')
devtools::install_github("SPRFMO/jjmR")

if(!'kableExtra' %in% installed.packages()) install.packages('kableExtra')
```

You'll need to be in the `jjm/assessment` directory in order for the code here to run.

```{r pkgs, echo=T}
library(jjmR)
library(tidyverse)
library(kableExtra)

# MP note: normally I never use setwd in rmarkdown because it has unexpected behaviour. 
# I thought you would always end up in the jjm rootdirectory if you start up the markdown file?
# I cannot change the working directory by using setwd() ??

pwd <- getwd()
# if (!grepl(basename(pwd), "assessment", ignore.case = TRUE)) {
#   stop(paste("Set working directory to jjm/assessment"))
# }

geth <- function(mod,h=hyp) paste0(h,"_", mod) # Package? Or keep?

```

# Re-running Last Year's Model (a sanity check)
Re-running the `r as.numeric(format(Sys.time(), "%Y"))-1` model and comparing the results with that year's SC meeting.


## Single-stock hypothesis {.tabset}
```{r load_prev_h1}
hyp <- "h1"

# mod0.00 <- runit(geth("0.00"),pdf=TRUE,portrait=F,est=TRUE,exec="../src/jjms")
mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

# mod_prev <- readJJM(geth("1.00"), path = "config", input = "input")
# save(mod_prev, file="results/mod_prev_h1.Rdat")

load("results/mod_prev_h1.Rdat")

```
### Biomass

```{r biomass_h1_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

oldnewMods <- combineModels(mod0.00,mod_prev)

plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h1_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```


### Fishing Mortality
```{r fmort_h1_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Incremental Data Updates

The most updated table of model runs can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

## Updating last year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))-1` include catch estimates, age and length compositions, and indices of abundance. 

```{r}
mods2compare <- c("0.00","0.01","0.02","0.03", "0.04")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h1"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}

plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Updating this year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))` include projected catch estimates, age and length compositions, and indices of abundance. 

Currently, only the Chilean and Offshore CPUE indices have been made available (to me at least).

```{r}
mods2compare <- c("0.04","0.05","0.06","0.07", "0.08")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datcurr, fig.cap=paste0("Plot comparing biomass estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
hyp <- "h1"
Dat_Curr <- compareModels(geth(mods2compare))

plot(Dat_Curr,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datcurr, fig.cap=paste0("Plot comparing recruitment estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
plot(Dat_Curr,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datcurr, fig.cap=paste0("Plot comparing fishing mortality estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}

plot(Dat_Curr,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


# Other Business
## General
* Reweighting of data for Chile CPUE, Offshore CPUE?
	- Use sample sizes to weight the age data
* Age-0 data
* Anything that stands out? Any particularly egregious errors?
* How to do projection for h2?

## Other models to run
* 2-stock hypothesis runs
* Update control file to 2021
* Projection runs (recruitment regimes)




