---
title: "Jack Mackerel Assessment SC12 (Preliminary)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir=here::here())
knitr::opts_chunk$set(warning=F, message=F, echo=F, results=F,fig.width=6, fig.height=5)
```

This document was compiled in `RMarkdown`, and shows the incremental results of the Chilean Jack Mackerel (*Trachurus murphyi*) stock assessment update in `r format(Sys.time(), "%Y")`. The files associated with this document can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

The code to create the input files for this assessment and to run these models can be found in [`jjm/assessment/R/SC12_Bridging.R`](https://github.com/SPRFMO/jjm/tree/master/assessment/R/SC12_Bridging.R). Should you choose to run the models, please ensure that you have:

* Compiled the latest `jjm/src/jjms.tpl`
  - This can be done by navigating to the `jjm/src` folder in your Terminal, and using the `make` command
  - You will need to have [ADMB](http://www.admb-project.org/) installed to do this.
  - This does not need to be done if you're only re-compiling the R Markdown document.
* Updated the `jjmR` package
  - This can be done in `R` using the command `remotes::install_github("SPRFMO/jjmR")`

```{r install_packages, eval=F, cache=F, echo=T}
if(!'devtools' %in% installed.packages()) install.packages('devtools')
devtools::install_github("SPRFMO/jjmR")

if(!'kableExtra' %in% installed.packages()) install.packages('kableExtra')
```

```{r pkgs, echo=T}
library(jjmR)
library(tidyverse)
library(kableExtra)
library(patchwork)
theme_set(theme_jjm(base_size = 15))

pwd <- getwd()

fn_plotind <- function(mods2compare, indname) {
  fn_seldata <- function(x) {
  x$data$Index[,i] %>%
    bind_rows() %>%
    pivot_longer(everything(), names_to="year") %>%
    drop_na() %>%
    mutate(year=as.numeric(year),
            assessment_year=max(year))
  }

  mods <- compareModels(geth(mods2compare, "h1"))
  i <- grep(indname,mods[[1]]$data$Inames)
  dat2use <- list()
  for(m in 1:length(mods)) {
    dat2use[[m]] <- fn_seldata(mods[[m]])
  }

  p <- map_dfr(dat2use, ~as_tibble(.)) %>%
        mutate(assessment_year=as.factor(assessment_year)) %>%
        ggplot() +
          geom_line(aes(x=year,y=value,colour=assessment_year)) +
          scale_x_continuous(breaks= scales::pretty_breaks())
  print(p)
}

finmodname <- "1.07"

```


# Model Naming Convention
File naming conventions have been changed to reflect the stock structure hypotheses associated with each run. The `h1` denotes the single-stock hypothesis, while `h2` denotes the two-stock one.


```{r results = "asis"}
modruns <- read_csv(here::here("data", "SC12_runs.csv"))

modruns %>% 
  kable() %>%
  kable_styling() %>%
  row_spec(0, bold = TRUE, background = "#05427b", color = "white") %>%
  row_spec(1, bold = TRUE, background = "#05427b", color = "white") %>%
  row_spec(13, bold = TRUE, background = "#05427b", color = "white") %>%
  row_spec(22, bold = TRUE, background = "#05427b", color = "white")
```

You'll need to be in the `jjm/assessment` directory in order for the code here to run.


# Re-running Last Year's Model (a sanity check)
Re-running the `r as.numeric(format(Sys.time(), "%Y"))-1` model and comparing the results with that year's SC meeting.


## Single-stock hypothesis {.tabset}
```{r load_prev_h1}
hyp <- "h1"

h1_mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

load("results/mod_prev_h1.Rdat")
names(mod_prev_h1) <- mod_prev_h1[[1]]$control$modelName <- "mod_prev"

```
### Biomass

```{r biomass_h1_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev_h1), ") with a re-run of the model this year (", names(h1_mod0.00),").")}

oldnewMods <- combineModels(h1_mod0.00, mod_prev_h1) %>%
                changeNameModel(c("SC11 mod0.00","SC10 mod1.02"))
plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h1_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev_h1), ") with a re-run of the model this year (", names(h1_mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev_h1), ") with a re-run of the model this year (", names(h1_mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```
## Two-stock hypothesis {.tabset}
```{r load_prev_h2}
hyp <- "h2"
h2_mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

# mod_prev <- readJJM(geth("1.00"), path = "config", input = "input")
# save(mod_prev, file="results/mod_prev_h2.Rdat")

load("results/mod_prev_h2.Rdat")
names(mod_prev_h2) <- mod_prev_h2[[1]]$control$modelName <- "mod_prev"

```

### Biomass

```{r biomass_h2_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev_h2), ") with a re-run of the model this year (", names(h2_mod0.00),").")}

oldnewMods <- combineModels(h2_mod0.00,mod_prev_h2) %>%
                changeNameModel(geth(c("SC11 mod0.00","SC10 mod1.02")))

plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h2_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev_h2), ") with a re-run of the model this year (", names(h2_mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```


### Fishing Mortality
```{r fmort_h2_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev_h2), ") with a re-run of the model this year (", names(h2_mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Incremental Data Updates

The most updated table of model runs can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

## Updating last year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))-1`, includes catch estimates, age and length compositions, and indices of abundance.

```{r}
mods2compare <- c("0.00","0.01","0.02","0.03", "0.04")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h1"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Two-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h2_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1],"h2"), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h2"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h2_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h2_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}

plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Updating this year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))` include projected catch estimates, age and length compositions, and indices of abundance. 

```{r}
mods2compare <- c("0.04","0.05","0.06","0.07", "0.08", "0.09", "0.09","0.10")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datcurr, fig.cap=paste0("Plot comparing biomass estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
hyp <- "h1"
Dat_Curr <- compareModels(geth(mods2compare))

plot(Dat_Curr,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datcurr, fig.cap=paste0("Plot comparing recruitment estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
plot(Dat_Curr,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datcurr, fig.cap=paste0("Plot comparing fishing mortality estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}

plot(Dat_Curr,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h2_datcurr, fig.cap=paste0("Plot comparing biomass estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
hyp <- "h2"
Dat_Curr <- compareModels(geth(mods2compare))

plot(Dat_Curr,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h2_datcurr, fig.cap=paste0("Plot comparing recruitment estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
plot(Dat_Curr,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h2_datcurr, fig.cap=paste0("Plot comparing fishing mortality estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}

plot(Dat_Curr,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Stepping through the CPUE replacements
### SC Chile CPUE
```{r, fig.height=3}
mods2compare <- c("0.07", "0.08")

fn_plotind(mods2compare, "Chile_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
Chile_CPUE <- compareModels(geth(mods2compare, "h1"))

plot(Chile_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Chile_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}

plot(Chile_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Chile_CPUE <- compareModels(geth(mods2compare))

plot(Chile_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Chile_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Chile_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Peru CPUE
```{r, fig.height=3}
mods2compare <- c("0.08", "0.09")

fn_plotind(mods2compare, "Peru_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h1"
Peru_CPUE <- compareModels(geth(mods2compare))

plot(Peru_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Peru_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}

plot(Peru_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Peru_CPUE <- compareModels(geth(mods2compare))

plot(Peru_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Peru_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Peru_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Offshore CPUE
```{r, fig.height=3}
mods2compare <- c("0.03", "0.04")

fn_plotind(mods2compare, "Offshore_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h1"
Offshore_CPUE <- compareModels(geth(mods2compare))

plot(Offshore_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Offshore_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Offshore_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Offshore_CPUE <- compareModels(geth(mods2compare))

plot(Offshore_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Offshore_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Offshore_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Final Data Update
This just shows the final data update, using the exact same model (i.e., with the same control files).

```{r}
mods2compare <- c("0.00","0.10")
```

## Single-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h1_datfin, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
hyp <- "h1"
dat_fin <- compareModels(geth(mods2compare))

plot(dat_fin,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h1_datfin, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
plot(dat_fin,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}

plot(dat_fin,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h2_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
hyp <- "h2"
dat_fin <- compareModels(geth(mods2compare))

plot(dat_fin,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h2_datfin, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
plot(dat_fin,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h2_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}

plot(dat_fin,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Model Update
These results are from updating the model to include selectivity changes in the most recent year, and to extend the recruitment regime shift time series. This was the same procedure that was applied in previous years.

```{r}
mods2compare <- c("0.00","1.00")
```
## Single-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h1_base, fig.cap=paste0("Plot comparing biomass estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
hyp <- "h1"
Mod_Update <- compareModels(geth(mods2compare))

plot(Mod_Update,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h1_base, fig.cap=paste0("Plot comparing recruitment estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
plot(Mod_Update,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_base, fig.cap=paste0("Plot comparing fishing mortality estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}

plot(Mod_Update,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h2_base, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
hyp <- "h2"
Mod_Update <- compareModels(geth(mods2compare))

plot(Mod_Update,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h2_base, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
plot(Mod_Update,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h2_base, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model  (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}

plot(Mod_Update,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

---

# Sensitivity Analyses
The code used to run the following sensitivities (1.01 onwards) can be found in `assessment/R/SC12.R`.

```{r results = "asis"}
modruns %>%
  slice(13:n()) %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1, bold = TRUE, background = "#203c64", color = "white")

```

## Changing selectivity and catchability for Offshore fishery in 2021
The dynamics of the offshore fleet changed significantly in 2021, with the fishery fishing further north than they had in the past. Previous asssessments had accepted base models with added flexibility in selectivity for 2022 (SC10-1.02) and a downweighted offshore CPUE value in 2022 (SC11-1.07). For this sensitivity, we moved that selectivity flexibility to 2021 and added a break in catchability for the same year, while increasing the CV for the entire CPUE time series to be the same as that of previous years.

```{r}
mods2compare <- c("1.00","1.01")
mod_cap <- "from adding flexibility to selectivity and catchability for the offshore fishery in 2021."
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
hyp <- "h1"
res <- compareModels(geth(mods2compare))
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r, fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}
plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Fit to Survey
```{r}
p1 <- res_tidy$index_fits %>%
  filter(fleet_name == "Offshore_CPUE") %>%
  ggplot() + 
    geom_pointrange(aes(year, observed_ind, ymin = observed_ind - 1.96 * observed_se, ymax =  observed_ind + 1.96 * observed_se), alpha = 0.5) +
    geom_path(aes(year, pred_ind, colour = model)) + 
    scale_x_continuous(name = "Year") + 
    scale_y_continuous(name = "Index Values")
print(p1)
```

#### Fit to Age Composition
```{r}
p1 <- res_tidy$age_fits %>%
  filter(fleet_name == "Offshore_Trawl") %>% 
  ggplot() +
    geom_col(aes(x = age, y = observed)) +
    geom_line(aes(x = age, y = predicted, colour = model)) +
    facet_wrap(~year)

print(p1)
```

#### Catchability Coefficients
```{r}
p1 <- res_tidy$catchabilities %>%
  filter(fleet_name == "Offshore_CPUE") %>% 
  ggplot() +
    geom_line(aes(x = year, y = q, colour = model))

print(p1)
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates  ", mod_cap)}
hyp <- "h2"
res <- compareModels(geth(mods2compare))
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}

plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Fit to Survey
```{r}
p1 <- res_tidy$index_fits %>%
  filter(fleet_name == "Offshore_CPUE") %>%
  ggplot() + 
    geom_pointrange(aes(year, observed_ind, ymin = observed_ind - 1.96 * observed_se, ymax =  observed_ind + 1.96 * observed_se), alpha = 0.5) +
    geom_path(aes(year, pred_ind, colour = model)) + 
    scale_x_continuous(name = "Year") + 
    scale_y_continuous(name = "Index Values")
print(p1)
```

#### Fit to Age Composition
```{r}
p1 <- res_tidy$age_fits %>%
  filter(fleet_name == "Offshore_Trawl") %>% 
  ggplot() +
    geom_col(aes(x = age, y = observed)) +
    geom_line(aes(x = age, y = predicted, colour = model)) +
    facet_wrap(~year)

print(p1)
```

#### Catchability Coefficients
```{r}
p1 <- res_tidy$catchabilities %>%
  filter(fleet_name == "Offshore_CPUE") %>% 
  ggplot() +
    geom_line(aes(x = year, y = q, colour = model))

print(p1)
```

## Chilean CPUE standardised with spatio-temporal Bayesian models (SC12-JM06)
This was also run as a sensitivity in SC11 (SC11-1.05). A 1% effort creep factor was applied to this time series.

### Comparing z-scored indices

```{r}
mods2compare <- c("1.00","1.02","1.03")
res <- compareModels(geth(mods2compare, "h1"))
res_tidy <- tidy_JJM(res)

mod_cap <- " from replacing the Chilean CPUE index with that from SC11-JM07."
```

```{r}
p1 <- res_tidy$index_fits %>%
  filter(fleet_name == "Chile_CPUE") %>%
  group_by(model) %>%
  mutate(z_obs = (observed_ind-mean(observed_ind))/sd(observed_ind)) %>%
  ggplot() +
    geom_path(aes(x = year, y = z_obs, colour = model))

print(p1)
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r, fig.cap=paste0("Plot comparing fishing mortality estimates  ", mod_cap)}
plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Fit to Survey
```{r}
p1 <- res_tidy$index_fits %>%
  filter(fleet_name == "Chile_CPUE") %>%
  ggplot() + 
    geom_pointrange(aes(year, observed_ind, ymin = observed_ind - 1.96 * observed_se, ymax =  observed_ind + 1.96 * observed_se, colour = model), alpha = 0.5) +
    geom_path(aes(year, pred_ind, colour = model)) + 
    scale_x_continuous(name = "Year") + 
    scale_y_continuous(name = "Index Values")
print(p1)
```

#### Fit to Age Composition
```{r}
p1 <- res_tidy$age_fits %>%
  filter(fleet_name == "SC_Chile_PS") %>% 
  ggplot() +
    geom_col(aes(x = age, y = observed)) +
    geom_line(aes(x = age, y = predicted, colour = model)) +
    facet_wrap(~year) 

print(p1)
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates  ", mod_cap)}
hyp <- "h2"
res <- compareModels(geth(mods2compare))
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}

plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Fixing some data and modelling errors
Peru noted a difference in treatment of selectivity between the Northern Chile fleet and the other three fleets - selectivity was not allowed to vary in the final year of the model. This was likely due to an oversight during SC6, and was corrected in model 1.04. Some anomalies were also noted in the age composition data for the Chilean acoustic north survey and the northern Chile fishery, where age-0 fish were recorded in the first two quarters of the year. This resulted in some corrections to the present year data, and were incorporated into the data-bridging exercise. More errors were found in data from earlier years, which were then corrected in model 1.05.

```{r}
mods2compare <- c("1.01", "1.04", "1.05")
res <- compareModels(geth(mods2compare, "h1"))
res_tidy <- tidy_JJM(res)

mod_cap <- "from correcting model and data for the Northern Chile fishing fleet and the Acoustic North survey."
```


### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r, fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}
plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
hyp <- "h2"
res <- compareModels(geth(mods2compare))
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}

plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Increasing confidence in the acoustic north survey
It was noted during SC12 that the acoustic north survey had consistently provided data in recent years.

```{r}
mods2compare <- c("1.05", "1.06")
res <- compareModels(geth(mods2compare, "h1"))
res_tidy <- tidy_JJM(res)

mod_cap <- "from correcting model and data for the Northern Chile fishing fleet and the Acoustic North survey."
```


### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r, fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}
plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
hyp <- "h2"
res <- compareModels(geth(mods2compare))
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}

plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Decreasing confidence in the current year's CPUE values
It was noted during SC12 that the CPUE values for the current year only reflected the dynamics for the first half of the assessment year. As such, they may not be reflective of the abundance trends of that year. As such, the CPUE value of the current year should be given less weight than those of previous years.

```{r}
mods2compare <- c("1.06", "1.07")
res <- compareModels(geth(mods2compare, "h1"))
res_tidy <- tidy_JJM(res)

mod_cap <- "from downweighting the value for CPUE in the current year for all CPUE series."
```


### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r, fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}
plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
hyp <- "h2"
res <- compareModels(geth(mods2compare))
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}

plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


---

# Final Model
Model `r finmodname` was selected as the final model for `r format(Sys.time(), "%Y")`.

## Comparison to last year
```{r}
h1nm <- geth(finmodname,"h1")

h1_mod <- readJJM(h1nm, path = "config", input = "input")
h1_diag <- diagnostics(h1_mod,plot=F)

res <- combineModels(h1_mod0.00, h1_mod)
res_tidy <- tidy_JJM(res)

mod_cap <- "from last year's model with the final model selected for this year."
```


### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r, fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}
plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
h2nm <- geth(finmodname,"h2")

h2_mod <- readJJM(h2nm,path = "config", input = "input")
h2_diag <- diagnostics(h2_mod, plots=F)
h2_bmsy_diag <- diagnostics(fixed_bmsy(h2_mod), plots = F)

res <- combineModels(h2_mod0.00, h2_mod)
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}

plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Model Diagnostics

### Single-Stock Hypothesis
```{r results=F}
new_bmsy <- mean(rev(h1_mod[[1]]$output[[1]]$msy_mt[,10])[1:10])

```

The $B_{MSY}$ for this year (an average of the most recent ten years) will be ***`r round(new_bmsy)/1000`*** million tons.

#### Fits to Data {.tabset}
##### Fishery Age Composition
```{r}
plot(h1_diag, var = "ageFitsCatch")
```

##### Fishery Length Composition
```{r}
plot(h1_diag, var = "lengthFitsCatch")
```

##### Survey Age Composition
```{r}
plot(h1_diag, var = "ageFitsSurvey")
```

##### Index Data
```{r}
plot(h1_diag, var = "predictedObservedIndices")
```

#### Projections {.tabset}

Projections done under a conservative recruitment regime (steepness 0.65, recruitment curve estimated from 2001:2015).

##### SSB
```{r}
h1_mod_ls <- readJJM(paste0(h1nm,".ls"), path="config", input="input")
h1_diag_ls <- diagnostics(h1_mod_ls, plots=F)
plot(h1_diag_ls, var = "ssbPrediction")
```

##### Catch
```{r}
plot(h1_diag_ls, var = "catchPrediction")
```

#### Kobe Plot
```{r, fig.width=8, fig.cap=paste0("BMSY fixed at ", round(new_bmsy)/1000, " million tons.")}
kobe(fixed_bmsy(h1_mod), engine="ggplot")
```

#### Summary Plot
```{r, fig.cap=paste0("BMSY fixed at ", round(new_bmsy)/1000, " million tons, shown by the orange line. The blue lines show the reference points estimated by the model.")}
bmsy_diag <- diagnostics(fixed_bmsy(h1_mod), plots = F)
plot(bmsy_diag, var = "summarySheet")
```


### Two-Stock Hypothesis

```{r results=F}
new_bmsy_s <- mean(rev(h2_mod[[1]]$output[[1]]$msy_mt[,10])[1:10])
new_bmsy_n <- mean(rev(h2_mod[[1]]$output[[2]]$msy_mt[,10])[1:10])

```

The $B_{MSY}$ for this year (an average of the most recent ten years) will be ***`r round(new_bmsy_s)/1000`*** million tons for the south stock and ***`r round(new_bmsy_n)/1000`*** million tons for the north stock.


#### Fits to Data {.tabset}
##### Fishery Age Composition
```{r}
plot(h2_diag, var = "ageFitsCatch")
```

##### Fishery Length Composition
```{r}
plot(h2_diag, var = "lengthFitsCatch")
```

##### Survey Age Composition
```{r}
plot(h2_diag, var = "ageFitsSurvey")
```

##### Index Data
```{r}
plot(h2_diag, var = "predictedObservedIndices")
```

#### Projections {.tabset}
Projections done under a conservative recruitment regime (steepness 0.65, recruitment curve estimated from 2001:2015).

##### SSB
```{r}
h2_mod_ls <- readJJM(paste0(h2nm,".ls"), path="config", input="input")
h2_diag_ls <- diagnostics(h2_mod_ls, plots=F)
plot(h2_diag_ls, var = "ssbPrediction")
```

##### Catch
```{r}
plot(h2_diag_ls, var = "catchPrediction")
```


#### Kobe Plot
```{r, fig.width=8, fig.cap=paste0("BMSY fixed at ", round(new_bmsy_s)/1000, " million tons for the south stock and ", round(new_bmsy_n)/1000, " million tons for the north stock.")}
kobe(fixed_bmsy(h2_mod), engine="ggplot") + facet_wrap(~stock, scale="free")
```

#### Summary Plot
```{r, fig.cap=paste0("BMSY fixed at ", round(new_bmsy_s)/1000, " million tons for the south stock and ", round(new_bmsy_n)/1000, "million tons for the north stock, shown as the orange line. The blue lines show the reference points estimated by the model.")}
plot(h2_bmsy_diag, var = "summarySheet")
```

## Likelihood Table
```{r results="asis"}
finmods <- combineModels(h1_mod, h2_mod)
LL <- summary(finmods)$like

knitr::kable(LL) %>% kableExtra::kable_styling()
```

# Other Business
## Data needs

## General

## Other models to run?
