---
title: "Jack Mackerel Assessment SC13 (Preliminary)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir=here::here())
knitr::opts_chunk$set(warning=F, message=F, echo=F, results=F,fig.width=6, fig.height=5)
```

This document was compiled in `RMarkdown`, and shows the incremental results of the Chilean Jack Mackerel (*Trachurus murphyi*) stock assessment update in `r format(Sys.time(), "%Y")`. The files associated with this document can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

The code to create the input files for this assessment and to run these models can be found in [`jjm/assessment/R/SC13_Bridging.R`](https://github.com/SPRFMO/jjm/tree/master/assessment/R/SC12_Bridging.R). Should you choose to run the models, please ensure that you have:

* Compiled the latest `jjm/src/jjms.tpl`
  - This can be done by navigating to the `jjm/src` folder in your Terminal, and using the `make` command
  - You will need to have [ADMB](http://www.admb-project.org/) installed to do this.
  - This does not need to be done if you're only re-compiling the R Markdown document.
* Updated the `jjmR` package
  - This can be done in `R` using the command `remotes::install_github("SPRFMO/jjmR")`

```{r install_packages, eval=F, cache=F, echo=T}
if(!'devtools' %in% installed.packages()) install.packages('devtools')
devtools::install_github("SPRFMO/jjmR")

if(!'kableExtra' %in% installed.packages()) install.packages('kableExtra')
```

```{r pkgs, echo=T}
library(jjmR)
library(tidyverse)
library(kableExtra)
library(patchwork)
theme_set(theme_jjm(base_size = 15))

pwd <- getwd()

fn_plotind <- function(mods2compare, indname) {

  fn_seldata <- function(x, i) {
    x$data$Index[,i] %>%
      bind_rows() %>%
      pivot_longer(everything(), names_to="year") %>%
      drop_na() %>%
      mutate(year=as.numeric(year),
              assessment_year=max(year)
      )
  }  

  mods <- compareModels(geth(mods2compare, "h1"))
  i <- grep(indname,mods[[1]]$data$Inames)
  dat2use <- list()
  for(m in 1:length(mods)) {
    dat2use[[m]] <- fn_seldata(mods[[m]],i)
  }

  p <- map_dfr(dat2use, ~as_tibble(.)) %>%
        mutate(assessment_year=as.factor(assessment_year)) %>%
        ggplot() +
          geom_line(aes(x=year,y=value,colour=assessment_year)) +
          scale_x_continuous(breaks= scales::pretty_breaks())
  print(p)
}

finmodname <- "1.00"

```


# Model Naming Convention
File naming conventions have been changed to reflect the stock structure hypotheses associated with each run. The `h1` denotes the single-stock hypothesis, while `h2` denotes the two-stock one.


```{r results = "asis"}
modruns <- read_csv(here::here("data", "SC13_runs.csv"))

ind <- which(str_detect(modruns$Model, "Models"))

modruns %>% 
  kable() %>%
  kable_styling() %>%
  row_spec(0, bold = TRUE, background = "#05427b", color = "white") %>%
  row_spec(ind, bold = TRUE, background = "#05427b", color = "white")
```

You'll need to be in the `jjm/assessment` directory in order for the code here to run.


# Re-running Last Year's Model (a sanity check)
Re-running the `r as.numeric(format(Sys.time(), "%Y"))-1` model and comparing the results with that year's SC meeting.


## Single-stock hypothesis {.tabset}
```{r load_prev_h1}
hyp <- "h1"

h1_mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

load("results/mod_prev_h1.Rdat")
names(mod_prev_h1) <- mod_prev_h1[[1]]$control$modelName <- "mod_prev"

```
### Biomass

```{r biomass_h1_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev_h1), ") with a re-run of the model this year (", names(h1_mod0.00),").")}

oldnewMods <- combineModels(h1_mod0.00, mod_prev_h1) %>%
                changeNameModel(c("SC11 mod0.00","SC10 mod1.02"))
plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h1_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev_h1), ") with a re-run of the model this year (", names(h1_mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev_h1), ") with a re-run of the model this year (", names(h1_mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```
## Two-stock hypothesis {.tabset}
```{r load_prev_h2}
hyp <- "h2"
h2_mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

# mod_prev <- readJJM(geth("1.00"), path = "config", input = "input")
# save(mod_prev, file="results/mod_prev_h2.Rdat")

load("results/mod_prev_h2.Rdat")
names(mod_prev_h2) <- mod_prev_h2[[1]]$control$modelName <- "mod_prev"

```

### Biomass

```{r biomass_h2_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev_h2), ") with a re-run of the model this year (", names(h2_mod0.00),").")}

oldnewMods <- combineModels(h2_mod0.00,mod_prev_h2) %>%
                changeNameModel(geth(c("SC11 mod0.00","SC10 mod1.02")))

plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h2_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev_h2), ") with a re-run of the model this year (", names(h2_mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```


### Fishing Mortality
```{r fmort_h2_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev_h2), ") with a re-run of the model this year (", names(h2_mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Incremental Data Updates

The most updated table of model runs can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

## Updating last year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))-1`, includes catch estimates, age and length compositions, and indices of abundance.

```{r}
mods2compare <- c("0.00","0.01","0.02","0.03", "0.04")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h1"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Two-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h2_datprev, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1],"h2"), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
hyp <- "h2"
Dat_Prev <- compareModels(geth(mods2compare))

plot(Dat_Prev,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h2_datprev, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}
plot(Dat_Prev,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h2_datprev, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))-1,".")}

plot(Dat_Prev,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Updating this year's data
The data updated to `r as.numeric(format(Sys.time(), "%Y"))` include projected catch estimates, age and length compositions, and indices of abundance. 

```{r}
mods2compare <- c("0.04","0.05","0.06","0.07", "0.08", "0.09", "0.09","0.10")
```

### Single-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h1_datcurr, fig.cap=paste0("Plot comparing biomass estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
hyp <- "h1"
Dat_Curr <- compareModels(geth(mods2compare))

plot(Dat_Curr,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h1_datcurr, fig.cap=paste0("Plot comparing recruitment estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
plot(Dat_Curr,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h1_datcurr, fig.cap=paste0("Plot comparing fishing mortality estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}

plot(Dat_Curr,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, biomass_h2_datcurr, fig.cap=paste0("Plot comparing biomass estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
hyp <- "h2"
Dat_Curr <- compareModels(geth(mods2compare))

plot(Dat_Curr,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, recruitment_h2_datcurr, fig.cap=paste0("Plot comparing recruitment estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}
plot(Dat_Curr,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fmort_h2_datcurr, fig.cap=paste0("Plot comparing fishing mortality estimated with last year's data using the same model (", geth(mods2compare[1]),") but with data updated to ",as.numeric(format(Sys.time(), "%Y")),".")}

plot(Dat_Curr,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Stepping through the CPUE replacements
### SC Chile CPUE
```{r, fig.height=3}
mods2compare <- c("0.07", "0.08")

fn_plotind(mods2compare, "Chile_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
Chile_CPUE <- compareModels(geth(mods2compare, "h1"))

plot(Chile_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Chile_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}

plot(Chile_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Chile_CPUE <- compareModels(geth(mods2compare))

plot(Chile_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Chile_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Chile_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Peru CPUE
```{r, fig.height=3}
mods2compare <- c("0.08", "0.09")

fn_plotind(mods2compare, "Peru_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h1"
Peru_CPUE <- compareModels(geth(mods2compare))

plot(Peru_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Peru_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}

plot(Peru_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Peru_CPUE <- compareModels(geth(mods2compare))

plot(Peru_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Peru_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Peru_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

### Offshore CPUE
```{r, fig.height=3}
mods2compare <- c("0.03", "0.04")

fn_plotind(mods2compare, "Offshore_CPUE")

```

#### Single-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h1"
Offshore_CPUE <- compareModels(geth(mods2compare))

plot(Offshore_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Offshore_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Offshore_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

#### Two-stock hypothesis {.tabset}
##### Biomass
```{r}
hyp <- "h2"
Offshore_CPUE <- compareModels(geth(mods2compare))

plot(Offshore_CPUE,combine=T,what="biomass",stack=F,main="Biomass")
```

##### Recruitment
```{r}
plot(Offshore_CPUE,combine=T,what="recruitment",stack=F,main="Recruitment")
```

##### Fishing Mortality
```{r}
plot(Offshore_CPUE,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Final Data Update
This just shows the final data update, using the exact same model (i.e., with the same control files).

```{r}
mods2compare <- c("0.00","0.10")
```

## Single-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h1_datfin, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
hyp <- "h1"
dat_fin <- compareModels(geth(mods2compare))

plot(dat_fin,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h1_datfin, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
plot(dat_fin,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}

plot(dat_fin,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h2_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
hyp <- "h2"
dat_fin <- compareModels(geth(mods2compare))

plot(dat_fin,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h2_datfin, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}
plot(dat_fin,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h2_datfin, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", geth(mods2compare[1]), ") with data updated to ",as.numeric(format(Sys.time(), "%Y"))," (",geth(mods2compare[2]),").")}

plot(dat_fin,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

# Model Update
These results are from updating the model to include selectivity changes in the most recent year, and to extend the recruitment regime shift time series. This was the same procedure that was applied in previous years.

```{r}
mods2compare <- c("0.00","1.00")
```
## Single-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h1_base, fig.cap=paste0("Plot comparing biomass estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
hyp <- "h1"
Mod_Update <- compareModels(geth(mods2compare))

plot(Mod_Update,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h1_base, fig.cap=paste0("Plot comparing recruitment estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
plot(Mod_Update,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_base, fig.cap=paste0("Plot comparing fishing mortality estimates from last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}

plot(Mod_Update,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}
### Biomass
```{r, biomass_h2_base, fig.cap=paste0("Plot comparing biomass estimated by last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
hyp <- "h2"
Mod_Update <- compareModels(geth(mods2compare))

plot(Mod_Update,combine=T,what="biomass",stack=F,main="Biomass")
```

### Recruitment
```{r, recruitment_h2_base, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}
plot(Mod_Update,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h2_base, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model  (", geth(mods2compare[1]), ") to this year's (",geth(mods2compare[2]),").")}

plot(Mod_Update,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

---

# Sensitivity Analyses
## Leave-one-in Analysis
Only indices with recent data are considered: CPUE indices for Chile, Peru and offshore, and Chile Acoustic N. Age composition data were left in.


|  Model |  Leaves In  |
|:-------|------------:|
| 1.01   | Chile CPUE |
| 1.02   | Offshore CPUE |
| 1.03   | Peru CPUE |
| 1.04   | Acoustic N Chile |
| 1.05   | Only recent years (>2000) of Acoustic N Chile  |

```{r}
mods2compare <- c("1.00","1.01", "1.02", "1.03", "1.04", "1.05")
mod_cap <- "from leaving one index abundance in."
```


### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
hyp <- "h1"
res <- compareModels(geth(mods2compare))
res_tidy <- tidy_JJM(res)

dw <- c("Chile_CPUE", "Offshore_CPUE", "Peru_CPUE", "Chile_AcousN")
plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Fit to Survey
```{r}
h1_tidy <- res_tidy$index_fits %>%
  filter(model == "h1_1.00") %>%
  mutate(low = observed_ind - 1.96 * observed_se, upp =  observed_ind + 1.96 * observed_se)

p1 <- res_tidy$index_fits %>%
  filter(fleet_name %in% dw) %>%
  left_join(h1_tidy) %>%
  ggplot() + 
    geom_pointrange(aes(year, observed_ind, ymin = low, ymax =  upp), alpha = 0.5) +
    geom_path(aes(year, pred_ind, colour = model)) + 
    scale_x_continuous(name = "Year") + 
    scale_y_continuous(name = "Index Values") +
    facet_wrap(vars(fleet_name), scales = "free_y")
print(p1)
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates  ", mod_cap)}
hyp <- "h2"
res <- compareModels(geth(mods2compare, "h2"))
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Fit to Survey
```{r}
h2_tidy <- res_tidy$index_fits %>%
  filter(model == "h2_1.00") %>%
  mutate(low = observed_ind - 1.96 * observed_se, upp =  observed_ind + 1.96 * observed_se)

p1 <- res_tidy$index_fits %>%
  filter(fleet_name %in% dw) %>%
  left_join(h2_tidy) %>%
  ggplot() + 
    geom_pointrange(aes(year, observed_ind, ymin = low, ymax =  upp), alpha = 0.5) +
    geom_path(aes(year, pred_ind, colour = model)) + 
    scale_x_continuous(name = "Year") + 
    scale_y_continuous(name = "Index Values") +
    facet_wrap(vars(fleet_name), scales = "free_y")
print(p1)
```


---

# Final Model
Model `r finmodname` was selected as the final model for `r format(Sys.time(), "%Y")`.

## Comparison to last year
```{r}
h1nm <- geth(finmodname,"h1")

h1_mod <- readJJM(h1nm, path = "config", input = "input")
h1_diag <- diagnostics(h1_mod,plot=F)

res <- combineModels(h1_mod0.00, h1_mod)
res_tidy <- tidy_JJM(res)

mod_cap <- "from last year's model with the final model selected for this year."
```


### Single-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r, fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}
plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```


### Two-stock hypothesis {.tabset}
#### Biomass
```{r, fig.cap=paste0("Plot comparing biomass estimates ", mod_cap)}
h2nm <- geth(finmodname,"h2")

h2_mod <- readJJM(h2nm,path = "config", input = "input")
h2_diag <- diagnostics(h2_mod, plots=F)
h2_bmsy_diag <- diagnostics(fixed_bmsy(h2_mod), plots = F)

res <- combineModels(h2_mod0.00, h2_mod)
res_tidy <- tidy_JJM(res)

plot(res,combine=T,what="biomass",stack=F,main="Biomass")
```

#### Recruitment
```{r, fig.cap=paste0("Plot comparing recruitment estimates ", mod_cap)}
plot(res,combine=T,what="recruitment",stack=F,main="Recruitment")
```

#### Fishing Mortality
```{r fig.cap=paste0("Plot comparing fishing mortality estimates ", mod_cap)}

plot(res,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Model Diagnostics

### Single-Stock Hypothesis
```{r results=F}
new_bmsy <- mean(rev(h1_mod[[1]]$output[[1]]$msy_mt[,10])[1:10])

```

The $B_{MSY}$ for this year (an average of the most recent ten years) will be ***`r round(new_bmsy)/1000`*** million tons.

#### Fits to Data {.tabset}
##### Fishery Age Composition
```{r}
plot(h1_diag, var = "ageFitsCatch")
```

##### Fishery Length Composition
```{r}
plot(h1_diag, var = "lengthFitsCatch")
```

##### Survey Age Composition
```{r}
plot(h1_diag, var = "ageFitsSurvey")
```

##### Index Data
```{r}
plot(h1_diag, var = "predictedObservedIndices")
```

#### Kobe Plot
```{r, fig.width=8, fig.cap=paste0("BMSY fixed at ", round(new_bmsy)/1000, " million tons.")}
kobe(fixed_bmsy(h1_mod), engine="ggplot")
```

#### Summary Plot
```{r, fig.cap=paste0("BMSY fixed at ", round(new_bmsy)/1000, " million tons, shown by the orange line. The blue lines show the reference points estimated by the model.")}
bmsy_diag <- diagnostics(fixed_bmsy(h1_mod), plots = F)
plot(bmsy_diag, var = "summarySheet")
```


### Two-Stock Hypothesis

```{r results=F}
new_bmsy_s <- mean(rev(h2_mod[[1]]$output[[1]]$msy_mt[,10])[1:10])
new_bmsy_n <- mean(rev(h2_mod[[1]]$output[[2]]$msy_mt[,10])[1:10])

```

The $B_{MSY}$ for this year (an average of the most recent ten years) will be ***`r round(new_bmsy_s)/1000`*** million tons for the south stock and ***`r round(new_bmsy_n)/1000`*** million tons for the north stock.


#### Fits to Data {.tabset}
##### Fishery Age Composition
```{r}
plot(h2_diag, var = "ageFitsCatch")
```

##### Fishery Length Composition
```{r}
plot(h2_diag, var = "lengthFitsCatch")
```

##### Survey Age Composition
```{r}
plot(h2_diag, var = "ageFitsSurvey")
```

##### Index Data
```{r}
plot(h2_diag, var = "predictedObservedIndices")
```

#### Kobe Plot
```{r, fig.width=8, fig.cap=paste0("BMSY fixed at ", round(new_bmsy_s)/1000, " million tons for the south stock and ", round(new_bmsy_n)/1000, " million tons for the north stock.")}
kobe(fixed_bmsy(h2_mod), engine="ggplot") + facet_wrap(~stock, scale="free")
```

#### Summary Plot
```{r, fig.cap=paste0("BMSY fixed at ", round(new_bmsy_s)/1000, " million tons for the south stock and ", round(new_bmsy_n)/1000, "million tons for the north stock, shown as the orange line. The blue lines show the reference points estimated by the model.")}
plot(h2_bmsy_diag, var = "summarySheet")
```

## Likelihood Table
```{r results="asis"}
finmods <- combineModels(h1_mod, h2_mod)
LL <- summary(finmods)$like

knitr::kable(LL) %>% kableExtra::kable_styling()
```

# Other Business
## Data needs
- Mean weight at age for F3
- F4 2025 projected catch data
  - Only using projections for EU
  - Korea and Russian Federation not fishing


## General

## Other models to run
- Leave one out for CPUE indices
- Selex change for 2025 offshore
- Selex change for 2025 Chile
