---
title: "Jack Mackerel Assessment SCW14"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

```{r setup, include=FALSE}
#knitr::opts_knit$set(root.dir=here::here())
knitr::opts_knit$set(root.dir=file.path(here::here()))
knitr::opts_chunk$set(warning=F, message=F, echo=F, results=F,fig.width=6, fig.height=5)
```

This document was compiled in `RMarkdown`, and shows the incremental results of the Chilean Jack Mackerel (*Trachurus murphyi*) stock assessment benchmark in `r format(Sys.time(), "%Y")`. The files associated with this document can be found on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment).

Annoted data files can be found in the Excel spreadsheet `newAge.xlsx` on [`jjm/assessment/data`](https://github.com/SPRFMO/jjm/tree/master/assessment/data).

* Compiled the latest `jjm/src/jjms.tpl`
  - This can be done by navigating to the `jjm/src` folder in your Terminal, and using the `make` command
  - You will need to have [ADMB](http://www.admb-project.org/) installed to do this.
  - This does not need to be done if you're only re-compiling the R Markdown document.
* Updated the `jjmR` package
  - This can be done in `R` using the command `remotes::install_github("SPRFMO/jjmR")`


# Model Naming Convention
File naming conventions have been changed to reflect the stock structure hypotheses associated with each run. The `h1` denotes the single-stock hypothesis, while `h2` denotes the two-stock one.

Model      | Description
-----------|--------------
**Models 0.x**| **Data introductions**
0.00     |  Exact 2020 (single stock `h1` and two-stock `h2`) model and data set through 2020 (mod1.0 from SC08)
0.01     |  As 0.00 but with revised catches through 2020 (currently still estimates)
0.02     |  As 0.01 but with updated 2020 fishery age composition data for N_Chile, SC_Chile, and Offshore_Trawl, and updated 2020 fishery length composition data for FarNorth
-----------|--------------
**Models 1.x**| **Updated Model and Sensitivities**
1.00     | Update model (selectivity changes, recruitment) to 2021; 0.10 data file
1.01     | As 1.00 but use revised data series "antiguo" of age composition and weight at age data for both Chilean fisheries and both Chilean acoustic surveys (assessment/NewAgeData/AgeDataInAssessment.csv)
1.02     | As 1.01 but incorporate revised (validated) age data for surveys and fleets with M and maturity updated (M=0.35) (NOT RUN)
1.03     | As 1.00 but with offshore CPUE that takes into account efficiency creep

```{r install_packages, eval=F, cache=F, echo=T}
if(!'devtools' %in% installed.packages()) install.packages('devtools')
devtools::install_github("SPRFMO/jjmR")

if(!'kableExtra' %in% installed.packages()) install.packages('kableExtra')
```

You'll need to be in the `jjm/assessment` directory in order for the code here to run.

```{r pkgs, echo=T}
library(jjmR)
library(tidyverse)
library(kableExtra)

# MP note: normally I never use setwd in rmarkdown because it has unexpected behaviour. 
# I thought you would always end up in the jjm rootdirectory if you start up the markdown file?
# I cannot change the working directory by using setwd() ??
# LQ It might depend on the programme you use to open the file? Would be great if someone could test if this runs.

pwd <- getwd()
# if (!grepl(basename(pwd), "assessment", ignore.case = TRUE)) {
#   stop(paste("Set working directory to jjm/assessment"))
# }

geth <- function(mod,h=hyp) paste0(h,"_", mod)

fn.plotind <- function(mods2compare, indname) {
  fn.seldata <- function(x) {
  x$data$Index[,i] %>%
    bind_rows() %>%
    pivot_longer(everything(), names_to="year") %>%
    drop_na() %>%
    mutate(year=as.numeric(year),
            assessment_year=max(year))
  }

  mods <- compareModels(geth(mods2compare, "h1"))
  i <- grep(indname,mods[[1]]$data$Inames)
  dat2use <- list()
  for(m in 1:length(mods)) {
    dat2use[[m]] <- fn.seldata(mods[[m]])
  }

  p <- map_dfr(dat2use, ~as_tibble(.)) %>%
        mutate(assessment_year=as.factor(assessment_year)) %>%
        ggplot(aes(x=year,y=value,colour=assessment_year)) +
        geom_line() +
        theme_minimal() + 
        scale_x_continuous(breaks= scales::pretty_breaks())
  print(p)
}

fixed_bmsy <- function(mod,refpt=5500){
  old_rat <- (mod[[1]]$output[[1]]$msy_mt[,13])
  new_rat <- (mod[[1]]$output[[1]]$msy_mt[,12]/ refpt)
  mod[[1]]$output[[1]]$msy_mt[,13] <- new_rat
  mod[[1]]$output[[1]]$msy_mt[,10] <- refpt
  return(mod)
}

FinModName <- "1.05"

```

# Re-running Last Year's Model (a sanity check)
Re-running the `r as.numeric(format(Sys.time(), "%Y"))-1` model and comparing the results with that year's SC meeting.


## Single-stock hypothesis {.tabset}
```{r load_prev_h1}
hyp <- "h1"

# mod0.00 <- runit(geth("0.00"),pdf=TRUE,portrait=F,est=TRUE,exec="../src/jjms")
mod0.00 <- readJJM(geth("0.00"), path = "config", input = "input")

# mod_prev <- readJJM(geth("1.00"), path = "config", input = "input")
# save(mod_prev, file="results/mod_prev_h1.Rdat")

load("results/mod_prev_h1.Rdat")

```
### Biomass

```{r biomass_h1_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

oldnewMods <- combineModels(mod0.00,mod_prev)

plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h1_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```

### Fishing Mortality
```{r fmort_h1_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```

## Two-stock hypothesis {.tabset}

```{r load_prev_h2}
hyp <- "h2"

# default model
mod0.02 <- readJJM(geth("0.02"), path = "config", input = "input")

# mod1.03 <- runit(geth("1.03"),pdf=TRUE,portrait=F,est=TRUE,exec="../src/jjms")
mod1.03 <- readJJM(geth("1.03"), path = "config", input = "input")

# load("results/mod_prev_h2.Rdat")

```

### Biomass

```{r biomass_h2_0.00 , fig.cap=paste0("Plot comparing biomass estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

oldnewMods <- combineModels(mod0.02,mod1.03)

plot(oldnewMods,combine=T,what="biomass",stack=F,main="Biomass")

```

### Recruitment
```{r recruit_h2_0.00, fig.cap=paste0("Plot comparing recruitment estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="recruitment",stack=F,main="Recruitment")
```


### Fishing Mortality
```{r fmort_h2_0.00, fig.cap=paste0("Plot comparing fishing mortality estimated by last year's model (", names(mod_prev), ") with a re-run of the model this year (", names(mod0.00),").")}

plot(oldnewMods,combine=T,what="ftot",stack=F,main="Total Fishing Mortality")
```




