---
title: "Example Chilean hoki and ling model applications"
output:
  html_document:
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir=here::here())
knitr::opts_chunk$set(warning=F, message=F)
```

The following model runs were based on a March 2023 external review held in Valparaiso, Chile 

# Chilean hoki


## Example model alternatives

Model      | Description
-----------|--------------
**Models 1.x**| **Simple example of some progressions from data in main CHOSAM model in 2022**
0.00     | 	Fixed acoustic survey q at 0.75, constant acoustic selectivity, steepness 0.65, Beverton holt estimated from SRR since 2000
0.01     | 	As 0.00 but with steepness estimated with mean 0.65, CV=0.2
0.02     | 	As 0.01 but with acoustic survey q estimated with prior mean at 0.75, CV=0.2
0.03     | 	As 0.02 but with added flexibility to acoustic survey
0.04     | 	As 0.03 but with SRR Estimated over 35 years (since 1986)
0.05     |  As 0.04 but with Ricker SRR

# Sensitivity Analyses
As mentioned in a previous document, sensitivity analyses occur after the bridging exercise is complete (although technically the bridging exercise is a sensitivity analysis itself- we're testing the sensitivity of the model to updates of individual pieces of data). The ones we'll talk about today will be examples taken from previous SC meetings.

# Comparing Model Runs {.tabset}
Before we jump into running examples, let's look at how to combine output from different models and compare them.

For example, now that we've gone through the bridging exercise, we might want to look at how the overall data update affected the model estimates certain quantities. As such, we will compare output from model 0.00 with model 0.10.

This code and more of the like can be found in `jjm/assessment/SC09.rmd`

```{r compare,eval=FALSE}
library(jjmR)
library(ggplot2)
library(tidyverse)
theme_set(theme_jjm(base_size = 15))

```

```{r, eval=F}
plot(h1h2)
```

## Biomass
```{r, eval=F}
plot(h1h2,combine=T,what="biomass",stack=F,main="Biomass")
```

## Recruitment
```{r, eval=F}
plot(h1h2,combine=T,what="recruitment",stack=F,main="Recruitment")
```

## Fishing Mortality
```{r, eval=F}
plot(h1h2,combine=T,what="ftot",stack=F,main="Fishing Mortality")
```

#

## Likelihood Tables
We can also easily create likelihood tables. Here, we are comparing likelihoods from the 1-stock and the 2-stock models (just an example; not sure if this comparison is valid).

```{r results="asis",eval=F}
LL <- summary(h1h2)$like

# Just for display purposes in this document
library(dplyr)
knitr::kable(LL) %>% kableExtra::kable_styling()
```

# Examples

Take a look at the tables of model runs listed on [Github](https://github.com/SPRFMO/jjm/tree/master/assessment) and let's select a few to go through.

Point to note: R scripts for sensitivity analyses were only made available during (and after?) SC9 (`jjm/assessment/R/SC09.R`). Previous years' analyses were done by hand.

# Exercises
- Every year, we run the final model using four different settings for estimating recruitment. They are:
    1. ll - **l**ow steepness (0.65) and **l**ong recruitment time series (1970-2015)
    1. ls - **l**ow steepness (0.65) and **s**hort recruitment time series (2000-2015)
    1. hl - **h**igh steepness (0.8) and **l**ong recruitment time series (1970-2015)
    1. hs - **h**igh steepness (0.8) and **s**hort recruitment time series (2000-2015)
  
  How would you run these scenarios? What files and what elements within it would you change?
    - Hint: There exists a `jjm/assessment/R/SC09_Projections.R` file, if you get stuck.

- Replace the SC_Chile_CPUE index with another time series (`jjm/assessment/data/SC09_CPUE_Chile_Trip.csv`).

```{r, eval=F}
library(tidyverse)
dat.chile.cpue <- read_csv(file.path("data/SC09_CPUE_Chile_Trip.csv"))
```
