---
title: "Title"
subtitle: "Subtitle"
format:
  docx:
    number-sections: false
execute: 
  echo: false
  warning: false
  message: false
  results: false
---

# Header 1
Body paragraph text?

## Header 2
Body paragraph 1.

Body paragraph 2.

### Header 3
How about some lists

- Point 1
- Point 2


#### Header 4
A numbered list

1. Numba one
1. Numba two
1. Numba three

## Tables

| Table Header 1   |Table Header 2     |
|-----------------:|:------------------|
| Markdown tables  | are pretty weird  |
|   But kinda fun  |     I guess       |
|  Right adjusted  |This should be left|

: This is a Markdown table caption. {#tbl-ref}

|  Table Header 1  |  Table Header 2  |
|:-----------------|-----------------:|
| 1                | a                |
| 2                | b                |

: This is a Markdown table with NUMBERS. {#tbl-ref-no}

This is a reference to @tbl-ref and @tbl-ref-no.

```{r}
#| label: tbl-kable
#| tbl-cap: This is a Kable Table.

library(tidyverse)
library(kableExtra)
tibble(Header_1 = c(1,2), Header_2 = c(3,4)) %>%
  kable()
```

Flextable does not like captions and Word documents. Causes some "unreadable" content that can be fixed by Word, but is very very annoying. Apparently it's a Quarto problem and there's nothing I can do about it. Whomp. But it adds extra header rows, which is very handy.

```{r}
library(flextable)
tibble(Header_1 = c(1,2), Header_2 = c(3,4)) %>%
  flextable()
```
