---
title: "JJM Assessment – Annex Figures"
format:
  html:
    toc: true
    toc-depth: 3
    theme: flatly
    embed-resources: true
    page-layout: full
    lightbox: true
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| label: setup
library(jjmR)
library(tidyverse)
source("annex_plot_helpers.R")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

h1nm <- "h1_0.07"
h2nm <- "h2_0.07"

h1_mod <- readJJM(h1nm, path = "../../assessment/config",
                  input = "../../assessment/input", output = "../../assessment/results")
h2_mod <- readJJM(h2nm, path = "../../assessment/config",
                  input = "../../assessment/input", output = "../../assessment/results")

h1_retro <- NULL
h1_retro_f <- file.path("../../assessment/results", paste0(h1nm, "_retrospective.RData"))
if (file.exists(h1_retro_f)) { load(h1_retro_f); h1_retro <- output }

h2_retro <- NULL
h2_retro_f <- file.path("../../assessment/results", paste0(h2nm, "_retrospective.RData"))
if (file.exists(h2_retro_f)) { load(h2_retro_f); h2_retro <- output }

#Sys.setenv(QUARTO_PATH = "C:/Users/NielsHintzen/AppData/Local/Programs/Quarto/bin/quarto.exe")

# Read real length bins (cm) from the shared input dat file
.lenbins <- read_lenbins(
  dat_path_from_ctl(h1nm, "../../assessment/config", "../../assessment/input")
)

# Cache composition data (used in eval guards and plot calls)
.h1_agefits_fsh <- extr_agefits_fsh(h1_mod)
.h2_agefits_fsh <- extr_agefits_fsh(h2_mod)
.h1_agefits_srv <- extr_agefits_srv(h1_mod)
.h2_agefits_srv <- extr_agefits_srv(h2_mod)
.h1_lenfits_fsh <- extr_lenfits_fsh(h1_mod, lenbins = .lenbins)
.h2_lenfits_fsh <- bind_rows(
  extr_lenfits_fsh(h2_mod, stock = 1, lenbins = .lenbins),
  extr_lenfits_fsh(h2_mod, stock = 2, lenbins = .lenbins)
)

# Cache index data
.h1_ind   <- extr_indices(h1_mod, stock = 1)
.h2_ind_1 <- extr_indices(h2_mod, stock = 1)
.h2_ind_2 <- extr_indices(h2_mod, stock = 2)

# Precompute max fig heights for dynamic-tab comp-fits chunks
.fsh_fleets_h1 <- unique(.h1_agefits_fsh$fleet)
.fsh_fleets_h2 <- unique(.h2_agefits_fsh$fleet)
.srv_srvs_h1   <- unique(.h1_agefits_srv$survey)
.srv_srvs_h2   <- unique(.h2_agefits_srv$survey)

.maxh_fsh_h1 <- max(4, sapply(.fsh_fleets_h1, \(fl) comp_fig_height(.h1_agefits_fsh, "fleet", fl)))
.maxh_fsh_h2 <- max(4, sapply(.fsh_fleets_h2, \(fl) comp_fig_height(.h2_agefits_fsh, "fleet", fl)))
.maxh_srv_h1 <- max(4, sapply(.srv_srvs_h1,   \(s)  comp_fig_height(.h1_agefits_srv, "survey", s)))
.maxh_srv_h2 <- max(4, sapply(.srv_srvs_h2,   \(s)  comp_fig_height(.h2_agefits_srv, "survey", s)))
.maxh_len_h1 <- max(4, comp_fig_height(.h1_lenfits_fsh))
.maxh_len_h2 <- max(4, comp_fig_height(.h2_lenfits_fsh))

# Precompute heights that need multi-step expressions (avoids {} in !expr YAML)
.effn_h1_height <- facet_fig_height(
  length(unique(paste(extr_effn(h1_mod)$name, extr_effn(h1_mod)$type))),
  ncol = 2, panel_h = 3)
.ind_h1_n  <- length(unique(.h1_ind$survey[!is.na(.h1_ind$obs)]))
.ind_h2_1_n <- length(unique(.h2_ind_1$survey[!is.na(.h2_ind_1$obs)]))
.ind_h2_2_n <- length(unique(.h2_ind_2$survey[!is.na(.h2_ind_2$obs)]))

# Fig height for Francis reweighting (same panel structure as effn, h2 only — h1 reuses .effn_h1_height)
.francis_h2_height <- facet_fig_height(
  length(unique(paste(extr_effn(h2_mod)$name, extr_effn(h2_mod)$type))),
  ncol = 2, panel_h = 3)

# Precompute Q-breaks per survey (used in individual diagnostic tabs)
.h1_qbreaks <- extr_q_breaks(h1_mod)
.h2_qbreaks <- extr_q_breaks(h2_mod)

# Survey counts for Q-trajectory plots (reuse cached index survey counts)
.qtraj_h1_n   <- .ind_h1_n
.qtraj_h2_1_n <- .ind_h2_1_n
.qtraj_h2_2_n <- .ind_h2_2_n

# Ridge plot heights (nrow=1 facets; height driven by year range of observed data)
.ridge_h <- function(df, type_col = "type") {
  n <- length(unique(df$year[df[[type_col]] == "observed"]))
  max(5, 1.5 + n * 0.13)
}
.ridge_age_fsh_h1 <- .ridge_h(.h1_agefits_fsh)
.ridge_age_fsh_h2 <- .ridge_h(.h2_agefits_fsh)
.ridge_age_srv_h1 <- .ridge_h(.h1_agefits_srv)
.ridge_age_srv_h2 <- .ridge_h(.h2_agefits_srv)
.ridge_len_fsh_h1 <- .ridge_h(.h1_lenfits_fsh)
.ridge_len_fsh_h2 <- .ridge_h(.h2_lenfits_fsh)
```

```{=html}
<script>
/* Lightbox fallback for knit_child tab plots that bypass Quarto's Lua filter.
   Quarto's lightbox: true only wraps figures processed through Pandoc (labeled,
   captioned chunks). Dynamic tab plots from knitr::knit_child() emit bare <img>
   tags; this script wraps them with a separate GLightbox instance at page load. */
window.addEventListener('load', function () {
  var imgs = document.querySelectorAll('.cell-output-display img:not(a img)');
  imgs.forEach(function (img) {
    var a = document.createElement('a');
    a.href = img.src;
    a.className = 'tab-lightbox';
    a.setAttribute('data-gallery', 'tab-plots');
    a.setAttribute('title', img.alt || '');
    img.parentNode.insertBefore(a, img);
    a.appendChild(img);
    img.style.cursor = 'zoom-in';
  });
  if (imgs.length > 0 && typeof GLightbox !== 'undefined') {
    GLightbox({ selector: '.tab-lightbox' });
  }
});
</script>
```

```{=html}
<style>
/* PFA green tab styling */
.panel-tabset .nav-tabs .nav-link.active,
.panel-tabset .nav-tabs .nav-link.active:focus,
.panel-tabset .nav-tabs .nav-link.active:hover {
  color: #004868;
  border-bottom-color: #00B764;
  border-top-color: transparent;
  border-left-color: transparent;
  border-right-color: transparent;
  font-weight: 600;
}
.panel-tabset .nav-tabs .nav-link:hover {
  color: #00B764;
  border-bottom-color: #00B764;
  border-top-color: transparent;
  border-left-color: transparent;
  border-right-color: transparent;
}
.panel-tabset .nav-tabs .nav-link {
  color: #004868;
}
.panel-tabset .nav-tabs {
  border-bottom-color: #00B764;
}
</style>
```

## Input Data

```{r}
#| label: fig-metadata
#| fig-cap: "Years and types of information used in the jack mackerel assessment models."
source("../../assessment/R/plot_metadataoverview.R")
print(p1)
```

```{r}
#| label: fig-effn
#| fig-cap: "Input sample sizes for all age and length composition data sources."
#| fig-height: !expr .effn_h1_height
plot_effn(h1_mod, stock = 1, title = jjm_label(h1nm))
```

```{r}
#| label: fig-catchbyfleet
#| fig-cap: "Catch of jack mackerel by fleet, with input catch CV (bottom panel)."
plot_catch_fleet(h1_mod, title = jjm_label(h1nm))
```

### Weight-at-age

::: {.panel-tabset}

#### Fisheries
```{r}
#| label: fig-wtatagefsh
#| fig-cap: !expr paste0("Mean weights-at-age (kg) over time used for the fisheries. Each line represents one age.")
#| fig-height: !expr facet_fig_height(length(unique(extr_wtat_fsh(h1_mod)$fleet)))
plot_wtat(extr_wtat_fsh(h1_mod), facet_var = "fleet", title = jjm_label(h1nm))
```

#### Surveys
```{r}
#| label: fig-wtatagesrv
#| fig-cap: !expr paste0("Mean weights-at-age (kg) over time used for the surveys. Each line represents one age.")
#| fig-height: !expr facet_fig_height(length(unique(extr_wtat_srv(h1_mod)$survey)))
plot_wtat(extr_wtat_srv(h1_mod), facet_var = "survey", title = jjm_label(h1nm))
```

#### Cohort – Fisheries
```{r}
#| label: fig-wtatcohortfsh
#| fig-cap: "Weight-at-age (kg) by cohort for the fisheries. Each line traces one cohort."
#| fig-height: !expr facet_fig_height(length(unique(extr_wtat_fsh(h1_mod)$fleet)))
plot_wtat_cohort(extr_wtat_fsh(h1_mod), facet_var = "fleet", title = jjm_label(h1nm))
```

#### Cohort – Surveys
```{r}
#| label: fig-wtatcohortsrv
#| fig-cap: "Weight-at-age (kg) by cohort for the surveys. Each line traces one cohort."
#| fig-height: !expr facet_fig_height(length(unique(extr_wtat_srv(h1_mod)$survey)))
plot_wtat_cohort(extr_wtat_srv(h1_mod), facet_var = "survey", title = jjm_label(h1nm))
```

:::

### Input age compositions

::: {.panel-tabset}

#### Fisheries – h1
```{r}
#| label: fig-ageridge-fsh-h1
#| fig-cap: !expr paste0("Observed age compositions by fishery – ", jjm_label(h1nm))
#| fig-height: !expr .ridge_age_fsh_h1
plot_comp_ridge(.h1_agefits_fsh, x_var = "age", facet_var = "fleet",
                x_lab = "Age", title = jjm_label(h1nm))
```

#### Fisheries – h2
```{r}
#| label: fig-ageridge-fsh-h2
#| fig-cap: !expr paste0("Observed age compositions by fishery – ", jjm_label(h2nm))
#| fig-height: !expr .ridge_age_fsh_h2
plot_comp_ridge(.h2_agefits_fsh, x_var = "age", facet_var = "fleet",
                x_lab = "Age", title = jjm_label(h2nm))
```

#### Surveys – h1
```{r}
#| label: fig-ageridge-srv-h1
#| fig-cap: !expr paste0("Observed age compositions by survey – ", jjm_label(h1nm))
#| fig-height: !expr .ridge_age_srv_h1
plot_comp_ridge(.h1_agefits_srv, x_var = "age", facet_var = "survey",
                x_lab = "Age", title = jjm_label(h1nm))
```

#### Surveys – h2
```{r}
#| label: fig-ageridge-srv-h2
#| fig-cap: !expr paste0("Observed age compositions by survey – ", jjm_label(h2nm))
#| fig-height: !expr .ridge_age_srv_h2
plot_comp_ridge(.h2_agefits_srv, x_var = "age", facet_var = "survey",
                x_lab = "Age", title = jjm_label(h2nm))
```

:::

### Input length compositions

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-lenridge-fsh-h1
#| eval: !expr has_comp(.h1_lenfits_fsh)
#| fig-cap: !expr paste0("Observed length compositions by fishery – ", jjm_label(h1nm))
#| fig-height: !expr .ridge_len_fsh_h1
plot_comp_ridge(.h1_lenfits_fsh, x_var = "length_bin", facet_var = "fleet",
                x_lab = "Length bin", title = jjm_label(h1nm))
```

#### Two-stock – h2
```{r}
#| label: fig-lenridge-fsh-h2
#| eval: !expr has_comp(.h2_lenfits_fsh)
#| fig-cap: !expr paste0("Observed length compositions by fishery – ", jjm_label(h2nm))
#| fig-height: !expr .ridge_len_fsh_h2
plot_comp_ridge(.h2_lenfits_fsh, x_var = "length_bin", facet_var = "fleet",
                x_lab = "Length bin", title = jjm_label(h2nm))
```

:::


## Index Diagnostics

::: {.panel-tabset}

### Single-stock – h1

```{r}
#| label: fig-indfitsh1
#| fig-cap: !expr paste0("Index fits overview – ", jjm_label(h1nm))
#| fig-height: !expr facet_fig_height(.ind_h1_n, ncol = 2, panel_h = 4.5)
plot_indices_v2(h1_mod, stock = 1, title = jjm_label(h1nm))
```

```{r}
#| label: fig-inddiagh1
#| results: asis
surveys <- .h1_ind |> filter(!is.na(obs), obs > 0, model > 0) |> pull(survey) |> unique()
out <- character(0)
for (s in surveys) {
  df_s <- filter(.h1_ind, survey == s, !is.na(obs), obs > 0, model > 0)
  if (nrow(df_s) == 0) next
  .df_s <- df_s
  .s_title <- paste0(s, " | ", jjm_label(h1nm))
  .byr <- .h1_qbreaks$break_year[.h1_qbreaks$survey == s]
  out <- c(out, knitr::knit_child(text = c(
    paste0("#### ", s, "\n"),
    "",
    "```{r, fig.height=8, echo=FALSE}",
    "plot_fit_diagnostics(.df_s, title = .s_title, break_years = .byr)",
    "```",
    ""
  ), envir = environment(), quiet = TRUE))
}
cat("::: {.panel-tabset}\n\n")
cat(paste(out, collapse = "\n"))
cat("\n\n:::\n\n")
```

### Two-stock – h2 – South stock

```{r}
#| label: fig-indfitsh2-1
#| fig-cap: !expr paste0("Index fits overview – ", jjm_label(h2nm, "South stock"))
#| fig-height: !expr facet_fig_height(.ind_h2_1_n, ncol = 2, panel_h = 4.5)
plot_indices_v2(h2_mod, stock = 1, title = jjm_label(h2nm, "South stock"))
```

```{r}
#| label: fig-inddiagh2-1
#| results: asis
surveys <- .h2_ind_1 |> filter(!is.na(obs), obs > 0, model > 0) |> pull(survey) |> unique()
out <- character(0)
for (s in surveys) {
  df_s <- filter(.h2_ind_1, survey == s, !is.na(obs), obs > 0, model > 0)
  if (nrow(df_s) == 0) next
  .df_s <- df_s
  .s_title <- paste0(s, " | ", jjm_label(h2nm, "South stock"))
  .byr <- .h2_qbreaks$break_year[.h2_qbreaks$survey == s]
  out <- c(out, knitr::knit_child(text = c(
    paste0("#### ", s, "\n"),
    "",
    "```{r, fig.height=8, echo=FALSE}",
    "plot_fit_diagnostics(.df_s, title = .s_title, break_years = .byr)",
    "```",
    ""
  ), envir = environment(), quiet = TRUE))
}
cat("::: {.panel-tabset}\n\n")
cat(paste(out, collapse = "\n"))
cat("\n\n:::\n\n")
```

### Two-stock – h2 – Far north stock

```{r}
#| label: fig-indfitsh2-2
#| fig-cap: !expr paste0("Index fits overview – ", jjm_label(h2nm, "Far north stock"))
#| fig-height: !expr facet_fig_height(.ind_h2_2_n, ncol = 2, panel_h = 4.5)
plot_indices_v2(h2_mod, stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

```{r}
#| label: fig-inddiagh2-2
#| results: asis
surveys <- .h2_ind_2 |> filter(!is.na(obs), obs > 0, model > 0) |> pull(survey) |> unique()
out <- character(0)
for (s in surveys) {
  df_s <- filter(.h2_ind_2, survey == s, !is.na(obs), obs > 0, model > 0)
  if (nrow(df_s) == 0) next
  .df_s <- df_s
  .s_title <- paste0(s, " | ", jjm_label(h2nm, "Far north stock"))
  .byr <- .h2_qbreaks$break_year[.h2_qbreaks$survey == s]
  out <- c(out, knitr::knit_child(text = c(
    paste0("#### ", s, "\n"),
    "",
    "```{r, fig.height=8, echo=FALSE}",
    "plot_fit_diagnostics(.df_s, title = .s_title, break_years = .byr)",
    "```",
    ""
  ), envir = environment(), quiet = TRUE))
}
cat("::: {.panel-tabset}\n\n")
cat(paste(out, collapse = "\n"))
cat("\n\n:::\n\n")
```

### Survey skill (ROC)

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-skill-h1
#| fig-cap: !expr paste0("Survey skill ROC curves – ", jjm_label(h1nm))
#| fig-height: !expr facet_fig_height(.qtraj_h1_n, ncol = 2, panel_h = 3.5)
plot_survey_skill(h1_mod, stock = 1, title = jjm_label(h1nm))
```

#### Two-stock – h2 – South stock
```{r}
#| label: fig-skill-h2-1
#| fig-cap: !expr paste0("Survey skill ROC curves – ", jjm_label(h2nm, "South stock"))
#| fig-height: !expr facet_fig_height(.qtraj_h2_1_n, ncol = 2, panel_h = 3.5)
plot_survey_skill(h2_mod, stock = 1, title = jjm_label(h2nm, "South stock"))
```

#### Two-stock – h2 – Far north stock
```{r}
#| label: fig-skill-h2-2
#| fig-cap: !expr paste0("Survey skill ROC curves – ", jjm_label(h2nm, "Far north stock"))
#| fig-height: !expr facet_fig_height(.qtraj_h2_2_n, ncol = 2, panel_h = 3.5)
plot_survey_skill(h2_mod, stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

:::

### Q-trajectories

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-qtraj-h1
#| fig-cap: !expr paste0("Catchability (q) trajectories – ", jjm_label(h1nm))
#| fig-height: !expr facet_fig_height(.qtraj_h1_n, ncol = 2, panel_h = 3)
plot_q_trajectory(h1_mod, stock = 1, title = jjm_label(h1nm))
```

#### Two-stock – h2 – South stock
```{r}
#| label: fig-qtraj-h2-1
#| fig-cap: !expr paste0("Q-trajectories – ", jjm_label(h2nm, "South stock"))
#| fig-height: !expr facet_fig_height(.qtraj_h2_1_n, ncol = 2, panel_h = 3)
plot_q_trajectory(h2_mod, stock = 1, title = jjm_label(h2nm, "South stock"))
```

#### Two-stock – h2 – Far north stock
```{r}
#| label: fig-qtraj-h2-2
#| fig-cap: !expr paste0("Q-trajectories – ", jjm_label(h2nm, "Far north stock"))
#| fig-height: !expr facet_fig_height(.qtraj_h2_2_n, ncol = 2, panel_h = 3)
plot_q_trajectory(h2_mod, stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

:::

:::


## Composition Diagnostics

::: {.panel-tabset}

### Age fits – Fisheries

::: {.panel-tabset}

#### Single-stock – h1

```{r}
#| label: fig-agefits-fsh-h1
#| results: asis
out <- character(0)
for (fl in .fsh_fleets_h1) {
  if (!has_comp(.h1_agefits_fsh, "fleet", fl)) next
  .fl <- fl
  out <- c(out, knitr::knit_child(text = c(
    paste0("##### ", fl, "\n"),
    "",
    paste0("```{r, fig.height=", .maxh_fsh_h1, ", echo=FALSE}"),
    "plot_comp_fits(.h1_agefits_fsh, 'age', 'fleet', .fl, 'Age', paste0(.fl, ' | ', jjm_label(h1nm)))",
    "```",
    ""
  ), envir = environment(), quiet = TRUE))
}
cat("::: {.panel-tabset}\n\n")
cat(paste(out, collapse = "\n"))
cat("\n\n:::\n\n")
```

#### Two-stock – h2

```{r}
#| label: fig-agefits-fsh-h2
#| results: asis
out <- character(0)
for (fl in .fsh_fleets_h2) {
  if (!has_comp(.h2_agefits_fsh, "fleet", fl)) next
  .fl <- fl
  out <- c(out, knitr::knit_child(text = c(
    paste0("##### ", fl, "\n"),
    "",
    paste0("```{r, fig.height=", .maxh_fsh_h2, ", echo=FALSE}"),
    "plot_comp_fits(.h2_agefits_fsh, 'age', 'fleet', .fl, 'Age', paste0(.fl, ' | ', jjm_label(h2nm)))",
    "```",
    ""
  ), envir = environment(), quiet = TRUE))
}
cat("::: {.panel-tabset}\n\n")
cat(paste(out, collapse = "\n"))
cat("\n\n:::\n\n")
```

:::

### Age fits – Surveys

::: {.panel-tabset}

#### Single-stock – h1

```{r}
#| label: fig-agefits-srv-h1
#| results: asis
out <- character(0)
for (s in .srv_srvs_h1) {
  if (!has_comp(.h1_agefits_srv, "survey", s)) next
  .s <- s
  out <- c(out, knitr::knit_child(text = c(
    paste0("##### ", s, "\n"),
    "",
    paste0("```{r, fig.height=", .maxh_srv_h1, ", echo=FALSE}"),
    "plot_comp_fits(.h1_agefits_srv, 'age', 'survey', .s, 'Age', paste0(.s, ' | ', jjm_label(h1nm)))",
    "```",
    ""
  ), envir = environment(), quiet = TRUE))
}
cat("::: {.panel-tabset}\n\n")
cat(paste(out, collapse = "\n"))
cat("\n\n:::\n\n")
```

#### Two-stock – h2

```{r}
#| label: fig-agefits-srv-h2
#| results: asis
out <- character(0)
for (s in .srv_srvs_h2) {
  if (!has_comp(.h2_agefits_srv, "survey", s)) next
  .s <- s
  out <- c(out, knitr::knit_child(text = c(
    paste0("##### ", s, "\n"),
    "",
    paste0("```{r, fig.height=", .maxh_srv_h2, ", echo=FALSE}"),
    "plot_comp_fits(.h2_agefits_srv, 'age', 'survey', .s, 'Age', paste0(.s, ' | ', jjm_label(h2nm)))",
    "```",
    ""
  ), envir = environment(), quiet = TRUE))
}
cat("::: {.panel-tabset}\n\n")
cat(paste(out, collapse = "\n"))
cat("\n\n:::\n\n")
```

:::

### Length fits

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-lenfitsfshh1
#| eval: !expr has_comp(.h1_lenfits_fsh)
#| fig-height: !expr .maxh_len_h1
plot_comp_fits(.h1_lenfits_fsh, x_var = "length_bin", grp_var = "fleet",
               x_lab = "Length bin", title = paste0("Length fits | ", jjm_label(h1nm)))
```

#### Two-stock – h2
```{r}
#| label: fig-lenfitsfshh2
#| eval: !expr has_comp(.h2_lenfits_fsh)
#| fig-height: !expr .maxh_len_h2
plot_comp_fits(.h2_lenfits_fsh, x_var = "length_bin", grp_var = "fleet",
               x_lab = "Length bin", title = paste0("Length fits | ", jjm_label(h2nm)))
```

:::

### Mean age

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-meanage-h1
#| fig-height: !expr facet_fig_height(length(unique(c(extr_meanage_fsh(h1_mod)$fleet, extr_meanage_srv(h1_mod)$survey))))
plot_meanstat(extr_meanage_fsh(h1_mod), facet_var = "fleet", y_lab = "Mean age (years)",
              title = paste0("Fisheries – ", jjm_label(h1nm)))
plot_meanstat(extr_meanage_srv(h1_mod), facet_var = "survey", y_lab = "Mean age (years)",
              title = paste0("Surveys – ", jjm_label(h1nm)))
```

#### Two-stock – h2
```{r}
#| label: fig-meanage-h2
#| fig-height: !expr facet_fig_height(length(unique(c(extr_meanage_fsh(h2_mod)$fleet, extr_meanage_srv(h2_mod)$survey))))
plot_meanstat(extr_meanage_fsh(h2_mod), facet_var = "fleet", y_lab = "Mean age (years)",
              title = paste0("Fisheries – ", jjm_label(h2nm)))
plot_meanstat(extr_meanage_srv(h2_mod), facet_var = "survey", y_lab = "Mean age (years)",
              title = paste0("Surveys – ", jjm_label(h2nm)))
```

:::

### Mean length

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-meanlen-h1
#| fig-height: !expr facet_fig_height(length(unique(extr_meanlen_fsh(h1_mod)$fleet)))
plot_meanstat(extr_meanlen_fsh(h1_mod), facet_var = "fleet", y_lab = "Mean length (cm)",
              title = jjm_label(h1nm))
```

#### Two-stock – h2
```{r}
#| label: fig-meanlen-h2
#| fig-height: !expr facet_fig_height(length(unique(extr_meanlen_fsh(h2_mod)$fleet)))
plot_meanstat(extr_meanlen_fsh(h2_mod), facet_var = "fleet", y_lab = "Mean length (cm)",
              title = jjm_label(h2nm))
```

:::

### Francis reweighting

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-francis-h1
#| fig-cap: !expr paste0("Francis T1.8 reweighting – ", jjm_label(h1nm))
#| fig-height: !expr .effn_h1_height
plot_francis(h1_mod, stock = 1, title = jjm_label(h1nm))
```

#### Two-stock – h2
```{r}
#| label: fig-francis-h2
#| fig-cap: !expr paste0("Francis T1.8 reweighting – ", jjm_label(h2nm))
#| fig-height: !expr .francis_h2_height
plot_francis(h2_mod, stock = 1, title = jjm_label(h2nm))
```

:::

:::


## Selectivity

::: {.panel-tabset}

### Single-stock – h1

::: {.panel-tabset}

#### Fisheries
```{r}
#| label: fig-selfshh1
#| fig-cap: !expr paste0("Selectivity by fishery – ", jjm_label(h1nm))
plot_sel_ridge(extr_sel_fsh(h1_mod), facet_var = "fleet", title = jjm_label(h1nm),
               breaks_df = extr_sel_breaks(h1_mod, "fsh"))
```

#### Surveys
```{r}
#| label: fig-selsrvh1
#| fig-cap: !expr paste0("Selectivity by survey – ", jjm_label(h1nm))
plot_sel_ridge(extr_sel_srv(h1_mod), facet_var = "survey", title = jjm_label(h1nm),
               breaks_df = extr_sel_breaks(h1_mod, "srv"))
```

:::

### Two-stock – h2

::: {.panel-tabset}

#### Fisheries
```{r}
#| label: fig-selfshh2
#| fig-cap: !expr paste0("Selectivity by fishery – ", jjm_label(h2nm))
plot_sel_ridge(extr_sel_fsh(h2_mod), facet_var = "fleet", title = jjm_label(h2nm),
               breaks_df = extr_sel_breaks(h2_mod, "fsh"))
```

#### Surveys
```{r}
#| label: fig-selsrvh2
#| fig-cap: !expr paste0("Selectivity by survey – ", jjm_label(h2nm))
plot_sel_ridge(extr_sel_srv(h2_mod), facet_var = "survey", title = jjm_label(h2nm),
               breaks_df = extr_sel_breaks(h2_mod, "srv"))
```

:::

:::


## Stock Status

### Summary sheets

::: {.panel-tabset}

#### Single-stock – h1

```{r}
#| label: fig-sumsheet-h1
#| fig-cap: !expr paste0("Summary sheet – ", jjm_label(h1nm))
#| fig-height: 8
plot_summary_sheet(fixed_bmsy(h1_mod), stock = 1, title = jjm_label(h1nm))
```

```{r}
#| label: fig-unfshbio-h1
#| fig-cap: !expr paste0("Fished vs unfished biomass – ", jjm_label(h1nm))
plot_fished_unfished(h1_mod, stock = 1, title = jjm_label(h1nm))
```

#### Two-stock – h2

```{r}
#| label: fig-sumsheet-h2-1
#| fig-cap: !expr paste0("Summary sheet – ", jjm_label(h2nm, "South stock"))
#| fig-height: 8
plot_summary_sheet(fixed_bmsy(h2_mod), stock = 1, title = jjm_label(h2nm, "South stock"))
```

```{r}
#| label: fig-sumsheet-h2-2
#| fig-cap: !expr paste0("Summary sheet – ", jjm_label(h2nm, "Far north stock"))
#| fig-height: 8
plot_summary_sheet(fixed_bmsy(h2_mod), stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

```{r}
#| label: fig-unfshbio-h2-1
#| fig-cap: !expr paste0("Fished vs unfished biomass – ", jjm_label(h2nm, "South stock"))
plot_fished_unfished(h2_mod, stock = 1, title = jjm_label(h2nm, "South stock"))
```

```{r}
#| label: fig-unfshbio-h2-2
#| fig-cap: !expr paste0("Fished vs unfished biomass – ", jjm_label(h2nm, "Far north stock"))
plot_fished_unfished(h2_mod, stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

:::


### Retrospective

::: {.panel-tabset}

#### Single-stock – h1

::: {.panel-tabset}

##### SSB
```{r}
#| label: fig-retro-ssb-h1
#| fig-cap: !expr paste0("Retrospective of SSB – ", jjm_label(h1nm))
#| eval: !expr isFALSE(is.null(h1_retro))
plot_retro(h1_retro, var = "SSB", stock = 1, title = jjm_label(h1nm))
```

##### Fbar
```{r}
#| label: fig-retro-f-h1
#| fig-cap: !expr paste0("Retrospective of fishing mortality – ", jjm_label(h1nm))
#| eval: !expr isFALSE(is.null(h1_retro))
plot_retro(h1_retro, var = "F", stock = 1, title = jjm_label(h1nm))
```

##### Recruitment
```{r}
#| label: fig-retro-r-h1
#| fig-cap: !expr paste0("Retrospective of recruitment – ", jjm_label(h1nm))
#| eval: !expr isFALSE(is.null(h1_retro))
plot_retro(h1_retro, var = "R", stock = 1, title = jjm_label(h1nm))
```

:::

#### Two-stock – h2

::: {.panel-tabset}

##### SSB
```{r}
#| label: fig-retro-ssb-h2
#| fig-cap: !expr paste0("Retrospective of SSB – ", jjm_label(h2nm))
#| fig-height: 8
#| eval: !expr isFALSE(is.null(h2_retro))
plot_retro(h2_retro, var = "SSB", stock = 1, title = jjm_label(h2nm, "South stock")) /
plot_retro(h2_retro, var = "SSB", stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

##### Fbar
```{r}
#| label: fig-retro-f-h2
#| fig-cap: !expr paste0("Retrospective of fishing mortality – ", jjm_label(h2nm))
#| fig-height: 8
#| eval: !expr isFALSE(is.null(h2_retro))
plot_retro(h2_retro, var = "F", stock = 1, title = jjm_label(h2nm, "South stock")) /
plot_retro(h2_retro, var = "F", stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

##### Recruitment
```{r}
#| label: fig-retro-r-h2
#| fig-cap: !expr paste0("Retrospective of recruitment – ", jjm_label(h2nm))
#| fig-height: 8
#| eval: !expr isFALSE(is.null(h2_retro))
plot_retro(h2_retro, var = "R", stock = 1, title = jjm_label(h2nm, "South stock")) /
plot_retro(h2_retro, var = "R", stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

:::

:::


### Historical retrospective

```{r}
#| label: histretro-source
#| include: false
pg <- NULL; pg2 <- NULL
histretro_f <- file.path("../../assessment", "R/plot_historicretro.R")
if (file.exists(histretro_f)) {
  local({
    owd <- setwd("../../assessment")
    on.exit(setwd(owd))
    source("R/plot_historicretro.R")
    pg  <<- pg
    pg2 <<- pg2
  })
}
```

::: {.panel-tabset}

#### SSB, F, Recruitment
```{r}
#| label: fig-histretroquants
#| fig-cap: !expr paste0("Historical retrospective of SSB, F, and recruitment from Model ",h1nm,".")
#| fig-height: 10
#| eval: !expr isFALSE(is.null(pg))
print(pg)
```

#### Reference points
```{r}
#| label: fig-histretrorefpts
#| fig-cap: !expr paste0("Historical retrospective of reference points from Model ",h1nm,".")
#| fig-height: 10
#| eval: !expr isFALSE(is.null(pg2))
print(pg2)
```

:::


### Kobe plots

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-kobe-h1
#| fig-cap: !expr paste0("Kobe plot – ", jjm_label(h1nm))
plot_kobe(h1_mod, stock = 1, title = jjm_label(h1nm))
```

#### Two-stock – h2
```{r}
#| label: fig-kobe-h2
#| fig-cap: !expr paste0("Kobe plots – ", jjm_label(h2nm))
#| fig-height: 8
plot_kobe(h2_mod, stock = 1, title = jjm_label(h2nm, "South stock")) /
plot_kobe(h2_mod, stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

:::


### Stock–recruitment

::: {.panel-tabset}

#### Single-stock – h1
```{r}
#| label: fig-sr-h1
#| fig-cap: !expr paste0("Stock–recruitment – ", jjm_label(h1nm))
plot_sr(h1_mod, stock = 1, title = jjm_label(h1nm))
```

#### Two-stock – h2
```{r}
#| label: fig-sr-h2
#| fig-cap: !expr paste0("Stock–recruitment – ", jjm_label(h2nm))
#| fig-height: 8
plot_sr(h2_mod, stock = 1, title = jjm_label(h2nm, "South stock")) /
plot_sr(h2_mod, stock = 2, title = jjm_label(h2nm, "Far north stock"))
```

:::

